\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures On}\\[5pt]
{\Large\bf Irregularities Of Distribution}\\[5cm]
\vskip 1cm


{\bf  By}
\medskip


{\large\bf  Wolfgang M. Schmidt}
\vfill


{\bf  Tata Institute of Fundamental Research,}

{\bf Bombay}

{\bf  1977}
\end{center}

\eject

\thispagestyle{empty}



\begin{center}
{\Large\bf Lectures On}\\[5pt]
{\Large\bf Irregularities Of Distribution}\\[5cm]
\vskip 1cm


{\bf  By}
\medskip


{\large\bf  Wolfgang M. Schmidt}
\vfill


{\bf  Notes by}
\medskip

{\large\bf  T. N. Shorey}
\vfill

{\bf  Tata Institute of Fundamental Research,}

{\bf  Bombay}

{\bf  1977}
\end{center}

\eject

\thispagestyle{empty}
\begin{center}
  ~
  \vfill

 {\bf \copyright \quad Tata Institute of Fundamental Research, 1977}\\
\vfill


\parbox{0.7\textwidth}{No part of this book may be reproduced in any form by print,
    microfilm or any other means without written permission form the
    Tata Institute of Fundamental Research, Colaba, Bombay 400005.}
\vfill


  Printed in India

  By

 {\bf K. P. Puthran at Tata Press Limited,}\\ 
  Bombay 400025\\
  and Published by  K. G. Ramanathan for the\\
  Tata Institute of Fundamental Research,\\
  Bombay 400005
\end{center}

\chapter{Preface}


These lectures were given at the Tata Institute of Fundamental
Research, Bombay, in the Fall of 1972. Excellent notes were taken by
T. N. Shorey. 

The theory of Irregularities of Distribution began as a branch of
Uniform Distributions, but is of independent interest. The papers
appearing in 1922 of Harday an Littlewood \cite{8} and of Ostrowski
\cite{16} on fractional parts of sequences $\alpha$, $2 \alpha,
\ldots$, may be regraded as forerunners of the general theory. The
first papers dealing with the distribution of general sequences $x_1,
x_2, \ldots$ are due to T. Van Aardenne Ehrenfest [1, 2] in 1945, 49,
and K. F. Roth \cite{19} in 1954. 

In these lectures I restricted myself to distribution problems with a
geometric interpretation. Unfortunately, because of lack of time, it
was not possible to include the important results of K. F. Roth on
irregularities of distribution of integer sequences with respect to
arithmetic progressions.  

\vskip 2cm
\noindent December, 1973 \hfill {\large\bf Wolfgang M. Schmidt}

\hfill Boulder, Colorado
 
