\chapter{South Asian Conference on Mathematical Education}

\begin{center}
{\bf BOMBAY, 22-28 FEBRUARY 1956}
\medskip

{\large\bf PROGRAMME}
\end{center}

\bigskip

\setcounter{pageoriginal}{16}
\begin{center}
{\bf Wednesday, February 22, 1956}\pageoriginale
\end{center}

\begin{longtable}[l]{r@{\;\;}l}
11.00 \textsc{a.m.} & Inauguration of the Conference\\[3pt]
                    & by Dr. H. J. Bhabha\\[8pt]
                    & Presidential address\\[3pt]
                    & by Professor K. Chandrasekharan\\[8pt]
3.30 \textsc{p.m.} --- 4.10 \textsc{p.m.} & Invited address\\[3pt]
                    & by Professor M. H. Stone on {\em Some crucial}\\
                    & {\em problems of mathematical instruction.}
\end{longtable}

\begin{center}
{\bf Thursday, February 23, 1956}
\end{center}

\begin{longtable}[l]{r@{\;\;}l}
9.45 \textsc{a.m.} --- 11.00 \textsc{a.m.} & Working Group (Post-graduate)\\[6pt]
11.15 \textsc{a.m.} --- 12.30 \textsc{p.m.} & Working Group (Graduate)\\[6pt]
3.30 \textsc{p.m.} --- 4.10 \textsc{p.m.} & Invited address\\[3pt]
                     & by Professor G. Choquet on {\em Teaching in}\\
                     & {\em secondary schools and research.}\\[8pt]
5.00 \textsc{p.m.} --- 5.40 \textsc{p.m.} & Invited address\\[3pt]
                  & by Professor T. A. A. Broadbent on\\
                  & {\em Present-day problems in English}\\
                  & {\em mathematical education.}
\end{longtable}

\begin{center}
{\bf Friday, February 24, 1956}
\end{center}
\begin{longtable}[l]{r@{\;\;}l}
9.45 \textsc{a.m.} --- 11.00 \textsc{a.m.} & Working Group (Undergraduate)\\[5pt]
11.15 \textsc{a.m.} --- 12.30 \textsc{p.m.} & Working Group (Undergraduate)\\[5pt]
2.30 \textsc{p.m.} --- 3.30 \textsc{p.m.} & Working Group (Graduate)\\[5pt]
3.45 \textsc{p.m.} --- 4.30 \textsc{p.m.} & Working Group (Post-graduate)
\end{longtable}

\begin{center}
{\bf Saturday, February 25, 1956}
\end{center}
\begin{longtable}[l]{r@{\;\;}l}
9.45 \textsc{a.m.} --- 11.00 \textsc{a.m.} & Plenary session\\[6pt]
11.30 \textsc{a.m.} --- 12.10 \textsc{p.m.} & Invited address\\[3pt]
              & by Professor A. Oppenheim on {\em The}\\
              & {\em problems which face mathematicians in}\\
              & {\em Singapore and the Federation of Malaya.}\\[8pt]
3.00 \textsc{p.m.} --- 3.40 \textsc{p.m.} & Invited address\\[3pt]
              & by Professor H. Freudenthal on\\
              & {\em Initiation into geometry.}\\[6pt]
4.30 \textsc{p.m.} --- 5.45 \textsc{p.m.} & Plenary session
\end{longtable}

\begin{center}
{\bf Sunday, February 26, 1956}
\end{center}
\begin{longtable}[l]{r@{\;\;}l}
10.00 \textsc{a.m.} --- 10.40 \textsc{a.m.} & Special lecture\\
               & by Professor A. D. Alexandrov on\\
               & {\em Mathematical education in the U.S.S.R.}\\[6pt]
11.15 \textsc{a.m.} --- 11.45 \textsc{a.m.} & Special lecture\\
          & by Professor G. Choquet on {\em New}\\
          & {\em material and a new method for the}\\
          & {\em teaching of elementary calculations in}\\
          & {\em primary schools.}
\end{longtable}

\begin{center}
{\bf Monday, February 27, 1956}
\end{center}
\begin{longtable}[l]{r@{\;\;}l}
9.45 \textsc{a.m.} --- 11.00 \textsc{a.m.} & Working Group (Post-graduate)\\[6pt]
11.15 \textsc{a.m.} --- 12.30 \textsc{p.m.} & Working Group (Graduate)\\[6pt]
3.00 \textsc{p.m.} --- 4.15 \textsc{p.m.} & Working Group (Undergraduate)\\[6pt]
5.00 \textsc{p.m.} --- 5.40 \textsc{p.m.} & Invited address\\
       & by Professor E. Bompiani on\\
       & {\em Mathematical instruction in Italy.}
\end{longtable}

\begin{center}
{\bf Tuesday, February 28, 1956}
\end{center}
\begin{longtable}[l]{r@{\;\;}l}
9.45 \textsc{a.m.} --- 10.25 \textsc{a.m.} & Invited address\\
         & by Professor T. A. A. Broadbent on\\
         & {\em Typography and the teaching of}\\
         & {\em mathematics.}\\[6pt]
11.15 \textsc{a.m.} --- 12.30 \textsc{p.m.} & Plenary session\\[6pt]
5.30 \textsc{p.m.} --- 5.40 \textsc{p.m.} & Special lecture\\
           & by Professor E. Marczewski on\\
           & {\em Mathematical education in Poland.}\\[6pt]
5.45 \textsc{p.m.} --- 6.00 \textsc{p.m.} & Special lecture\\
        & by professor H. F. Tuan on\\
        & {\em Mathematical education in}\\
        & {\em Chinese universities.}
\end{longtable}
