\chapter{South Asian Conference on Mathematical Education}

\begin{center}
{\bf BOMBAY, 22-28 FEBRUARY, 1956}
\medskip

{\large\bf LIST OF PARTICIPANTS}
\end{center}

\setcounter{pageoriginal}{180}
\pageoriginale
\renewcommand{\arraystretch}{1.23}
\begin{longtable}[l]{r@{\;\,}ll}
1. & Professor \textsc{Y. Akizuki} & (Japan)\\
2. & Professor \textsc{A. D. Alexandrov} & (U.S.S.R.)\\
3. & Professor \textsc{B. B. Bagi} & (India)\\
4. & Mr. \textsc{K. Balagangadharan} & (India)\\
5. & Professor \textsc{Ram Behari} & (India)\\
6. & Dr. \textsc{H. J. Bhabha} & (India)\\
7. & Professor \textsc{A. L. Blakers} & (Australia)\\
8. & Professor \textsc{S. Bochner} & (U.S.A.)\\
9. & Professor \textsc{E. Bompiani} & (Italy)\\
10. & Professor \textsc{T. A. A. Broadbent} & (U.K.)\\
11. & Professor \textsc{N. G. de Bruijn} & (The Netherlands)\\
12. & Professor \textsc{K. Chandrasekharan} & (India)\\
13. & Professor \textsc{G. L. Chandratreya} & (India)\\
14. & Professor \textsc{G. Choquet} & (France)\\
15. & Professor \textsc{S. Chowla} & (U.S.A.)\\
16. & Mr. \textsc{G. P. Darke} & (Singapore)\\
17. & Professor \textsc{B. C. Das} & (India)\\
18. & Professor \textsc{M. Deuring} & (W. Germany)\\
19. & Mr. \textsc{Saaduddin Djambek} & (Indonesia)\\
20. & Professor \textsc{M. Eichler} & (W. Germany)\\
21. & Professor \textsc{H. Freudenthal} & (The Netherlands)\\
22. & Dr. \textsc{K. S. Gangadharan} & (Ceylon)\\
23. & Professor \textsc{K. R. Gunjikar} & (India)\\
24. & Dr. \textsc{R. C. Gunning} & (U.S.A.)\\
25. & Professor \textsc{H. Gupta} & (India)\\
26. & Professor \textsc{Aung Hla} & (Burma)\\
27. & Professor \textsc{S. M. Kerawala} & (Pakistan)\\
28. & Dr. \textsc{M. Koecher} & (W. Germany)\\
29. & Professor \textsc{N. M. Korobov} & (U.S.S.R.)\\
30. & Dr. \textsc{V. S. Krishnan} & (India)\\
31. & Dr. \textsc{S. Kung} & (China)\\
32. & Professor \textsc{H. Maass} & (W. Germany)\\
33. & Professor \textsc{S. Mahadevan} & (India)\\
34. & Professor \textsc{S. Mandelbrojt} & (France)\\
35. & Mr. \textsc{S. D. Manerikar} & (India)\\
36. & Professor \textsc{E. Marczewski} & (Poland)\\
37. & Professor \textsc{S. Minakshisundaram} & (India)\\
38. & Drs. \textsc{Moerdomo} & (Indonesia)\\
39. & Professor \textsc{A. S. Monin} & (U.S.S.R.)\\
40. & Professor \textsc{P. H. Nagappa} & (India)\\
41. & Dr. \textsc{R. Naidu} & (India)\\
42. & Mr. \textsc{M. S. Narasimhan} & (India)\\
43. & Professor \textsc{A. Oppenheim} & (Malaya)\\
44. & Professor \textsc{H. Petersson} & (W. Germany)\\
45. & Mr. \textsc{Poerwadi Poerwadisastro} & (Indonesia)\\
46. & Dr. \textsc{B. N. Prasad} & (India)\\
47. & Professor \textsc{C. Racine} & (India)\\
48. & Professor \textsc{C. T. Rajagopal} & (India)\\
49. & Mr. \textsc{P. K. Raman} & (India)\\
50. & Dr. \textsc{K. G. Ramanathan} & (India)\\
51. & Professor \textsc{R. A. Rankin} & (U.K.)\\
52. & Professor \textsc{B. S. Madhava Rao} & (India)\\
53. & Mr. \textsc{V. V. Rao} & (India)\\
54. & Dr. \textsc{I. Satake} & (Japan)\\
55. & Professor \textsc{A. Selberg} & (U.S.A.)\\
56. & Dr. \textsc{D. K. Sen} & (India)\\
57. & Mr. \textsc{C. S. Seshadri} & (India)\\
58. & Professor \textsc{B. R. Seth} & (India)\\
59. & Dr. \textsc{N. G. Shabde} & (India)\\
60. & Professor \textsc{N. M. Shah} & (India)\\
61. & Professor \textsc{A. L. Shaikh} & (Pakistan)\\
62. & Professor \textsc{C. L. Siegel} & (W. Germany)\\
63. & Mr. \textsc{B. V. Singbal} & (India)\\
64. & Dr. \textsc{U. N. Singh} & (India)\\
65. & Mr. \textsc{Tharam Singh} & (Singapore)\\
66. & Mr. \textsc{Rabil Sitasuwana} & (Thailand)\\
67. & Professor \textsc{T. P. Srivastava} & (India)\\
68. & Professor \textsc{M. H. Stone} & (U.S.A.)\\
69. & Ir. \textsc{Suhakso} & (Indonesia)\\
70. & Professor \textsc{S. Tanbunyuen} & (Thailand)\\
71. & Professor \textsc{H. F. Tuan} & (China)\\
72. & Professor \textsc{P. Turan} & (Hungary)\\
73. & Professor \textsc{R. Vaidyanathaswamy} & (India)\\
74. & Professor \textsc{R. K. Vaish} & (India)\\
75. & Miss \textsc{H. K. Wong} & (Singapore)\\
\end{longtable}
