\chapter{South Asian Conference on Mathematical Education}

\begin{center}
{\bf BOMBAY, 22-28 FEBRUARY 1956}
\medskip

{\large\bf LIST OF PARTICIPANTS}
\end{center}
\medskip

\setcounter{pageoriginal}{8}
\noindent
\textsc{australia}\pageoriginale

\quad Professor \textsc{A. L. Blakers}

\quad University of Western Australia

\quad Perth
\medskip

\noindent
\textsc{burma}

\quad Professor \textsc{Aung Hla}

\quad University of Rangoon

\medskip

\noindent
\textsc{ceylon}

\quad Dr. \textsc{K. S. Gangadharan}

\quad University of Ceylon

\quad Colombo

\medskip

\noindent
\textsc{china}

\quad Dr. \textsc{S. Kung}

\quad University of Peking

\quad Professor \textsc{H. F. Tuan}

\quad University of Peking

\medskip

\noindent
\textsc{france}

\quad Professor \textsc{G. Choquet}

\quad Institut Henri Poincare

\quad 11, rue Pierre Curie

\quad Paris V
\smallskip

\quad Professor \textsc{S. Mandelbrojt}

\quad College de France

\quad Paris
\medskip

\noindent
\textsc{west germany}

\quad Professor \textsc{M. Deuring}

\quad University of G\"ottingen
\smallskip

\quad Professor \textsc{M. Eichler}\pageoriginale

\quad University of M\"unster
\smallskip

\quad Dr. \textsc{M. Koecher}

\quad University of M\"unster
\smallskip

\quad Professor \textsc{H. Maass}

\quad University of Heidelberg
\smallskip

\quad Professor \textsc{H. Petersson}

\quad University of M\"unster
\smallskip

\quad Professor \textsc{C. L. Siegel}

\quad University of G\"ottingen
\medskip

\noindent
\textsc{hungary}

\quad Professor \textsc{Paul Turan}

\quad University Matematikai Szeminariuma

\quad Budapest
\medskip

\noindent
\textsc{india}

\quad Professor \textsc{B. B. Bagi}

\quad Karnatak University
\smallskip

\quad Mr. \textsc{K. Balagangadharan}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Professor \textsc{Ram Behari}

\quad University of Delhi
\smallskip

\quad Dr. \textsc{H. J. Bhabha}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Professor \textsc{K. Chandrasekharan}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Professor \textsc{G. L. Chandratreya}

\quad University of Poona
\smallskip

\quad Professor \textsc{B. C. Das}\pageoriginale

\quad Utkal University
\smallskip

\quad Professor \textsc{K. R. Gunjikar}

\quad University of Bombay
\smallskip

\quad Professor \textsc{H. Gupta}

\quad Punjab University

\quad Hoshiarpur
\smallskip

\quad Dr. \textsc{V. S. Krishnan}

\quad University of Madras
\smallskip

\quad Professor \textsc{S. Mahadevan}

\quad Indian Mathematical Society

\quad Madras 4
\smallskip

\quad Mr. \textsc{S. D. Manerikar}

\quad University of Baroda
\smallskip

\quad Professor \textsc{S. Minakshisundaram}

\quad Andhra University

\quad Waltair
\smallskip

\quad Professor \textsc{P. H. Nagappa}

\quad University of Mysore
\smallskip

\quad Dr. \textsc{R. Naidu}

\quad Unesco Science Co-operation Office

\quad New Delhi
\smallskip

\quad Mr. \textsc{M. S. Narasimhan}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Dr. \textsc{B. N. Prasad}

\quad University of Allahabad
\smallskip

\quad Professor \textsc{C. Racine}

\quad Loyola College

\quad Madras 31
\smallskip

\quad Professor \textsc{C. T. Rajagopal}\pageoriginale

\quad Ramanujan Institute of Mathematics

\quad Madras 7
\smallskip

\quad Mr. P. K. Raman

\quad Tata Institute of Fundamental Research
\smallskip

\quad Dr. \textsc{K. G. Ramanathan}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Professor \textsc{B. S. Madhava Rao}

\quad Institute of Armament Studies

\quad Kirkee
\smallskip

\quad Mr. \textsc{V. V. Rao}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Dr. \textsc{D. K. Sen}

\quad University of Bombay
\smallskip

\quad Mr. \textsc{C. S. Seshadri}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Professor \textsc{B. R. Seth}

\quad Indian Institute of Technology

\quad Kharagpur
\smallskip

\quad Dr. \textsc{N. G. Shabde}

\quad University of Nagpur
\smallskip

\quad Professor \textsc{N. M. Shah}

\quad Baroda
\smallskip

\quad Dr. \textsc{U. N. Singh}

\quad Muslim University

\quad Aligarh
\smallskip

\quad Mr. \textsc{B. V. Singbal}

\quad Tata Institute of Fundamental Research
\smallskip

\quad Professor \textsc{T. P. Srivastava}

\quad University of Bihar
\smallskip

\quad Professor \textsc{T. P. Srivastava}\pageoriginale

\quad University of Bihar
\smallskip

\quad Professor \textsc{R. Vaidyanathaswamy}

\quad Sri Venkateswara University

\quad Tirupathi
\smallskip

\quad Professor \textsc{R. K. Vaish}

\quad University of Agra
\medskip

\noindent
\textsc{indonesia}

\quad Mr. \textsc{Saaduddin Djambek}

\quad Teacher Training Faculty

\quad Bandung
\smallskip

\quad Drs. \textsc{Moerdomo}

\quad University of Indonesia

\quad Bandung
\smallskip

\quad Mr. \textsc{Poerwadi Poerwadisastro}

\quad Senior High School

\quad Malang
\smallskip

\quad Ir. \textsc{Suhakso}

\quad University Gadjah-Mada

\quad Jogjakarta
\medskip

\noindent
\textsc{italy}

\quad Professor \textsc{E. Bompiani}

\quad Instituto Matematico

\quad Citt\`a Universitaria

\quad Rome
\medskip

\noindent
\textsc{japan}

\quad Professor \textsc{Y. Akizuki}

\quad Kyoto University

\quad Kyoto
\smallskip

\quad Dr. \textsc{I. Satake}\pageoriginale

\quad College of General Education

\quad University of Tokyo
\medskip

\noindent
\textsc{Malaya}

\quad Professor \textsc{A. Oppenheim}

\quad University of Malaya

\quad Singapore 10
\medskip

\noindent
\textsc{the netherlands}

\quad Professor \textsc{N. G. de Bruijn}

\quad Mathematisch Institut

\quad der Universiteit van Amsterdam
\smallskip

\quad Professor \textsc{H. Freudenthal}

\quad 44 Franz Schubertstraat

\quad Utrecht
\medskip

\noindent
\textsc{pakistan}

\quad Professor \textsc{S. M. Kerawala}

\quad University of Karachi
\smallskip

\quad Professor \textsc{A. L. Shaikh}

\quad University of Sind

\quad Hyderabad (Sind)
\medskip

\noindent
\textsc{poland}

\quad Professor \textsc{E. Marczewski}

\quad University of Wroclaw
\medskip

\noindent
\textsc{singapore}

\quad Mr. \textsc{G. P. Darke}

\quad Ministry of Education 
\smallskip

\quad Mr. \textsc{Tharam Singh}\pageoriginale

\quad Raffles Institution
\smallskip

\quad Miss \textsc{H. K. Wong}

\quad Teachers' Training College
\medskip

\noindent
\textsc{thailand}

\quad Professor \textsc{S. Tanbunyuen}

\quad Chulalongkorn University

\quad Bangkok
\smallskip

\quad Mr. \textsc{Rabil Sitasuwana}

\quad Department of Educational Technique

\quad Ministry of Education

\quad Bangkok
\medskip

\noindent
\textsc{united kingdom}

\quad Professor \textsc{T. A. A. Broadbent}

\quad Royal Naval College, Greenwich

\quad London S.E.10
\smallskip

\quad Professor \textsc{R. A. Rankin}

\quad The University

\quad Glasgow 2
\medskip

\noindent
\textsc{u.s.a.}

\quad Professor \textsc{S. Bochner}

\quad Fine Hall, Princeton University

\quad Pinceton, New Jersey
\smallskip

\quad Professor \textsc{S. Chowla}

\quad University of Colorado

\quad Boulder, Colorado
\smallskip

\quad Dr. \textsc{R. C. Gunning}

\quad Fine Hall, Princeton University

\quad Princeton, New Jersey
\smallskip

\quad Professor \textsc{A. Selberg}\pageoriginale

\quad The Instutute for Advanced Study

\quad Princeton, New Jersey
\smallskip

\quad Professor \textsc{M. H. Stone}

\quad Eckhart Hall

\quad University of Chicago

\quad Chicago 37, Illinois
\medskip

\noindent
\textsc{u.s.s.r.}

\quad Professor \textsc{A. D. Alexandrov}

\quad University of Leningrad
\smallskip

\quad Professor \textsc{N. M. Korobov}

\quad U.S.S.R. Academy of Sciences

\quad Moscow
\smallskip

\quad Professor \textsc{A. S. Monin}

\quad U.S.S.R. Academy of Sciences

\quad Moscow
