\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Stochastic Differential Equations}\\[5pt]
{\Large\bf and Malliavin Calculus}
\vskip 1cm

{\bf By}\\[5pt]
{\large\bf S. Watanabe}
\vfill


{\bf Tata Institute of Fundamental Research}\\
{\bf Bombay}\\
{\bf 1984}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Stochastic Differential Equations}\\[5pt]
{\Large\bf and Malliavin Calculus}
\vskip 1cm

{\bf By}
\medskip

{\large\bf S. Watanabe}
\vfill

{Lectures delivered at the}\\[5pt]
{\large\bf Indian Institute of Science, Bangalore}\\[7pt]
{under the }\\[7pt]
{\large\bf T.I.F.R.--I.I.Sc. Programme in Applications of}\\
{\large\bf Mathematics}

\vfill

{\bf Notes by}\\[5pt]
{\large\bf M. Gopalan Nair and B. Rajeev}

\vfill

{Published for the}\\
{\bf Tata Institute of Fundamental Research}\\
{\bf Springer-Verlag}\\
{Berlin Heidelberg New York Tokyo}\\
{\bf 1984}
\end{center}

\eject

\thispagestyle{empty}
\begin{center}
{\bf Author}\\[15pt]
{\large\bf S. Watanabe}\\
{Faculty of Science}\\
{Kyoto University}\\
{Kitashirakawa}\\
{Kyoto 606}\\
{\bf Japan}

\vfill

{\large\bf \copyright~ Tata Institute of Fundamental Research, 1984}\\

\vfill

\rule{\textwidth}{.5pt}

{ISBN 3-540-12897-2 Springer-Verlag. Berlin. Heidelberg.\\ New York. Tokyo} 

{ISBN 0-387-12897-2 Springer-Verlag. New  York. Heidelberg.\\ Berlin. Tokyo}

\rule{\textwidth}{.5pt}

\vfill

\parbox{0.7\textwidth}{
No part of this book may be reproduced in any form
by print, microfilm or any other means without
written permission from the Tata Institute of
Fundamental Research, Colaba, Bombay 400 005}

\vfill

Printed by M. N. Joshi at The Book Centre Limited,\\
Sion East, Bombay 400 022 and published by H. Goetze,\\
Springer-Verlag, Heidelberg, West Germany\\

\bigskip

{\bf Printed in India}

\end{center}

\eject

\thispagestyle{empty}

\chapter*{Preface}

These notes are based on six-week lectures given at T.I.F.R. Centre,
Indian Institute of Science, Bangalore, during February to April,
1983. My main purpose in these lectures was to study solutions of
stochastic differential equations as Wiener functionals and apply to
them some infinite dimensional functional analysis. This idea was due
to P. Malliavin. In the first part, I gave a calculus for Wiener
functionals, which may be of some independent interest. In the second
part, an application of this calculus to solutions of stochastic
differential equations is given, the main results of which are due to
Malliavin, Kusuoka and Stroock. I had no time to consider another
approach due to Bismut, in which more applications to filtering theory
and the regularity of boundary semigroups of diffusions are
discussed. 

\medskip

I would like to thank M. Gopalan Nair and B. Rajeev for their efforts
in completing these notes. Also I would like to express my gratitude
to Professor K.G. Ramanathan and T.I.F.R. for giving me this
opportunity to visit India. 
\vskip 1cm

\hfill{\large\bf S. Watanabe}
