\setcounter{chapter}{1}
\chapter{Weak and Strong Capacity}\label{p2:chap2}

\setcounter{section}{1}
\section{Weak capacity}\label{p2:chap2:sec2}%2

In\pageoriginale many applications it is not easy to verify the three
conditions of 
a true capacity, especially the second condition concerning the limit
of an increasing sequence of sets. We shall hence examine general
cases with stronger conditions which are more easily seen to be
fulfilled, and also other useful ``capacities'' which are not true
ones. We chiefly consider positive set functions which are the most
useful and the only ones we shall need later. 

\setcounter{defn}{3}
\begin{defn}\label{p2:chap2:sec2:def3}% def 4
  A real (finite or not ) set function $\varphi \geq 0$ defined on the
  family of all compact subsets of a Hausdorff space is said to be a
  weak capacity if  
  \begin{enumerate}[\rm (1)]
  \item $\varphi(K)$ is increasing with $K$
  \item For  any two compact sets $K_1$ and $K_2$
    $$
    \varphi(K_1 \cup K_2) \leq \varphi(K_1) + \varphi(K_2)
    $$
  \item $\varphi$ is continuous on the right for any compact set $K$
    with $\varphi (K) < + \infty$, that is to say for any $\varepsilon
    >0$, there exists an open set $\omega \supset K$, such that for
    any compact set $K' \subset \omega$ but containing $K, \varphi
    (K') \leq \varphi (K) + \varepsilon$.  
  \end{enumerate}
\end{defn}

Without using the condition (2), we shall derive the following
notions of ``inner and outer $\varphi$-capacities'' respectively in the
manner analogous to the derivation of the inner and outer measures
from content. 

We\pageoriginale define the inner capacity $\varphi_*$ and outer capacity $\varphi*$
of any set $A$ as  
\begin{align*}
  \varphi_* (A) &= \sup. \{ \varphi(K): \text{ Compact sets } K
  \subset A \}\\ 
  \varphi_* (A) &= \inf. \{\varphi_{*}(\omega) : \text{ Open sets }
  \omega \supset A \}. 
\end{align*}

When they are equal, the common value may be called capacity and denoted
$\varphi(A)$. Note that for open sets $\varphi_{*}$ and $\varphi^{*}$
are equal. 

Moreover it is true even of any compact set. For, $\varphi_{*}(K) =
\varphi(K)$ and it is enough to show that $\varphi (K) \geq
\varphi^*(K)$. For any $\varepsilon >0$, the right continuity of
$\varphi$ implies the existence of an open set $\omega_1 \supset K$
such that for any compact set $K' \subset \omega_1$ but containing
$K$, the inequality $\varphi(K') \leq \varphi(K) + \varepsilon
/2$. Hence $\varphi_{*} (\omega_1) \leq \varphi(K) + \varepsilon /2$
and $\varphi^{*}(K) \leq \varphi_{*} (\omega_1) \leq \varphi (K) +
\varepsilon /2$. This being true of arbitrary $\varepsilon > 0,
\varphi^{*}(K) \leq \varphi(K)$. 

Let us observe that the right continuity implies the condition $(3)$
of the definition of the true capacity. This comes from the fact that
if $\{K_n \}$ is a decreasing sequence of compact sets $(\cap K_n =
K)$ and $\omega$ any open set containing $K, K_n$ is contained in
$\omega$ for $n$ large enough. Further the two conditions [right
  continuity and $(3)$ of Def.1] are equivalent if the underlying
space is a locally compact metric one. 

\section{Properties of Inner and Outer capacities}\label{p2:chap2:sec3}%3

\begin{prop}\label{p2:chap2:sec3:prop1} % prop 1
  For\pageoriginale a weak capacity $\varphi, \varphi_* (\omega)$ is an increasing
  function of $\omega$ and for any increasing sequence of open sets
  $\omega_n$ 
  $$
  \varphi_*\left(\lim_{n \to \infty} \omega_n\right) = \lim_{n \to
    \infty} \varphi_*(\omega_n) 
  $$
\end{prop}

\begin{proof} % pro
  The increasing nature $\varphi_*$ is a consequence of the same
  property of $\varphi$. If $a < \varphi_*(\cup \omega_n)$, there
  exists a compact set $K$ contained in $\cup \omega_n$ such that
  $\varphi(K)> a$. We can find a positive integer $n_o$ such that $K
  \subset \omega_n$ for $n \geq n_o$. Hence $\varphi_* (\omega_n)>$a
  for $n \geq n_o$. Hence it follows that $\varphi_* (\cup \omega_n) =
  \lim \varphi_* (\omega_n)$. 
\end{proof}

\begin{prop}\label{p2:chap2:sec3:prop2} % prop 2
  $\varphi_*$ is countably subadditive on open sets.
\end{prop}

\begin{proof} % pro
  First let us prove that $\varphi_*$ is subadditive on open sets. Let
  $\omega_1$ and $\omega_2$ be any two open sets. For any $\lambda <
  \varphi_* (\omega_1 \cup \omega_2)$ we can find a compact set $K
  \subset \omega_1 \cup \omega_2$ such that $\varphi (K)
  >\lambda$. Now $K \cap C \omega_1$ and $K \cap C \omega_2$ do not
  intersect. They are contained in disjoint open subsets of $K$. The
  complements relative to $K$ of these two open sets give two open
  sets give two compact sets $K_1$ and $K_2, K_1 \subset \omega_1 K_2
  \subset \omega_2$ and $K_1 \cup K_2 =K$. 
  \begin{align*}
    & \varphi(K_1 \cup K_2) > \lambda\\
    & \varphi(K_1) + \varphi(K_2) > \lambda \text{ by subadditivity of
    } \varphi
  \end{align*}
  A fortiori \qquad $ \varphi_* (\omega_1) + \varphi_* (\omega_2) \lambda$

  This\pageoriginale being true of any $\lambda < \varphi_* (\omega_1 \cup \omega_2)$
  we have 
  $$
  \varphi_* (\omega_1) + \varphi_* (\omega_2) \geq \varphi_* (\omega_1
  \cup \omega_2).  
  $$
  Induction on $n$ and repeated application of the same inequality gives
  finite subadditivity. The countable subadditivity is then a
  consequence  of Proposition \ref{p2:chap2:sec3:prop1}. 
\end{proof}

\begin{prop}\label{p2:chap2:sec3:prop3} %pro 3
  The outer capacity $\varphi^*$ is countably subadditive.
\end{prop}

\begin{proof} % pro
  Let $A_n$ be any sequence of sets. If $\varphi^*(A_n) = + \infty$
  for any $n$ the proposition is immediate. We assume $\varphi^*(A_n)
  < + \infty$ for every $n$. Given $\epsilon > 0$, we can find open
  sets $\omega_n \supset A_n$ such that for every $n$ 
  \begin{gather*}
    \varphi^*(\omega_n)  \leq \varphi^*(A_n) + \frac{\varepsilon}{2^n}.\\
    \varphi^*\left(\bigcup^{\infty}_1 A_n\right)  \leq
    \varphi^*\left(\bigcup^{\infty}_1 \omega_n\right)  \leq \sum^{\infty}_1
    \varphi^*(A_n) + \varepsilon. 
  \end{gather*}
  $\varepsilon$ arbitrary, the proposition follows.
\end{proof}

\section{Strong Subadditivity}\label{p2:chap2:sec4} %%%4

In order to get a true capacity we shall introduce further
restrictions and first study the following notion of strong
subadditivity. 

\begin{defn}\label{p2:chap2:sec4:def5}% def 5
  Areal valued ($+ \infty$ being a possible value ) set function
  $\varphi > - \infty$ defined on a class $Phi$ of subsets of any
  fixed set, closed under finite unions and intersections, is said to
  be strongly subadditive if for any two $A$ and $B$ in $\Phi$ 
  $$
  \varphi(A \cup B)+ \varphi(A \cap B) \leq \varphi(A) + \varphi(B).
  $$
\end{defn}

\begin{prop}\label{p2:chap2:sec4:prop4}%prop 4
  For\pageoriginale a set function $\varphi > -\infty$ the increasing property and
  the strong subadditivity are together equivalent to either of the
  following inequalities: 
  \begin{enumerate}[(i)]
  \item For three sets $A_1,A_2$ and $X$ in $\Phi$,
    $$
    \varphi(X) + \varphi(X \cup A_1 \cup A_2) \leq \varphi(X \cup A_1)
    + \varphi(X \cup A_2). 
    $$
  \item For three sets $a,A$ and $K$ in $\Phi$, such that $a \subset A$,
    $$
    \varphi(A\cup K) + \varphi(a) \leq \varphi(a \cup K) + \varphi(A).
    $$
  \end{enumerate}
\end{prop}

In fact, the strong subadditivity for the sets $X \cup A_1$ and  $X
\cup A_2$ gives the inequality  
$$
\varphi( X \cup A_1 \cup A_2) + \varphi[X \cup (A_1 \cap A_2)] \leq
\varphi( X \cup A_1)+\varphi( X \cup A_2) 
$$

But $\varphi (X)  \varphi[X \cup (A_1 \cap A_2)]$ by increasing
property of $\varphi$ so that $(i)$ follows. 

Conversely, the substitution in $(i) :X = A \cap B, A_1 =A, A_2= B$
gives the strong subadditivity. 

The conditions (i) implies (ii) by taking in (i) $X =a \,A_1 =A, A_2
=K$ and the converse is seen by substituting $a=X, K =A_2$ and $A = A_1
\cup X$ in the inequality (ii). 

\begin{remark*} % rem
  Let $\psi$ be any finite real valued set function defined on the
  class $\Phi$ we have  considered.
\end{remark*}

Define\pageoriginale
\begin{align*}
  V_1 (X, A_1) &= \psi (X) - \psi (X \cup A_1)\\
  V_2 (X ; A_1, A_2) & = V_1 (X, A_1) - V_1 (X \cup A_2 ; A_1)\\
  \cdots \cdots & \cdots \cdots\cdots \cdots\\
  V_{n + 1} (X; A_1, A_2, \ldots A_{n + 1}) & = V_n (X ; A_1, \ldots,
  A_n) - V_n (X \cup A_{n + 1}, \ldots, A_n), 
\end{align*}
one may prove that $V_n \le 0$ implies $V_p \le 0$ for any $p \le n$
and that the assumption that $\chi$ is increasing and strongly
subadditive is equivalent to $V_2 \le 0$. The cases where $V_n \le 0$
for any $n$ or for any $n \le N$ are discussed by Choquet. 

\begin{prop}\label{p2:chap2:sec4:prop5}%pros 5
  If $\{A_i\}$ and $\{a_i\}$ are two finite families of sets of $\Phi$
  with $a_i \subset A_i$ for every $i$, then for any real valued set
  function $\varphi > - \infty$ defined on the class $\Phi$,
  increasing and strongly sub- additive, 
  $$
  \varphi (\cup A_i) + \sum \varphi (a_i) \le \varphi (\cup a_i) +
  \sum \varphi (A_i) 
  $$
\end{prop}

\begin{proof} % pro
  According to the proposition \ref{p2:chap2:sec4:prop4}, $(ii)$ :
  $$
  \displaylines{\hfill 
  \varphi (A_1 \cup A_2) + \varphi (a_1) \le \varphi (a_1 \cup A_2) +
  \varphi (A_1) \hfill \cr
  \text{and}\hfill \varphi (a_1 \cup A_2) + \varphi (a_2) \le \varphi (a_1
  \cup a_2) + \varphi (A_2)\hfill }
  $$
  hence we get required inequality when the families consist of two
  elements\pageoriginale each. [It is true even when $\varphi (a_1 \cup A_2) = +
  \infty $]. The general case follows by induction. 
\end{proof}

\section{Strong capacity}\label{p2:chap2:sec5}%sec 5

\begin{defn}\label{p2:chap2:sec5def6}% defi 6
  A weak capacity which is strongly subadditive on compact sets is
  called a strong capacity. 
\end{defn}

\begin{prop}\label{p2:chap2:sec5:prop6}%prop 6
  If $\varphi$ is a strong capacity then $\varphi_*$ is strongly
  subadditive on open sets and $\varphi^*$ is strongly subadditive. 
\end{prop}

\begin{proof} % pro
  Let $\omega_1$ and $\omega_2$ be two open sets ; $\alpha$ and
  $\beta$ two real numbers, $\alpha < \varphi_* (\omega_1 \cup
  \omega_2)$ and $\beta < \varphi_* (\omega_1 \cap \omega_2)$. We may
  find a compact set $K$ contained in $\omega_1 \cup \omega_2$ with
  decomposition into compact sets $K_1$ and $K_2$ such that $K = K_1
  \cup K_2, K_1 \subset \omega_1, K_2 \subset \omega_2, \varphi (K) >
  \alpha$ and $\varphi (K_1 \cap K_2) > \beta$. In fact we start with
  a compact set $K'$ contained in $\omega_1 \cup \omega_2$  and first
  get the decomposition $K^{'}_{1}$ and $K^{'}_{2}$ as in $(3)$. We
  enlarge $K^{'}_{1}$ and $K^{'}_{2}$ by union with a compact set $C$
  contained in $\omega_1 \cap \omega_2$ such that $\varphi (C) >
  \beta$. Now $K^{'}_{1} \cup C, K^{'}_{2} \cup C$ and their union
  fulfill our requirement. From 
  $$
  \varphi(K) + \varphi(K_1 \cap K_2) \le \varphi(K'_{1}) + \varphi (K_2)
  $$
  we deduce
  $$
  \alpha + \beta \le \varphi_* (\omega_1) + \varphi_* (\omega_2)
  $$
  and $\qquad \varphi_* (\omega_1 \cup \omega_2) + \varphi_* (\omega_1
  \cap \omega_2) \le \varphi_* (\omega_1) + \varphi_*(\omega_2)$. 
\end{proof}

Now\pageoriginale let $A_1$ and $A_2$ be any two sets. If $\varphi^* (A_1)$ and
$\varphi^*(A_2)$ finite, let us take arbitrary $\lambda_i > \varphi^*
(A_i)$. We can find open sets $\omega_1$ such that $\varphi_*
(\omega_i) < \lambda_i \,(i = 1, 2), \omega_i \supset A_i$ 
\begin{align*}
  \varphi^* (A_1 \cup A_2) + \varphi^* (A_1 \cap A_2) & \le  \varphi^*
  (\omega_1 \cup \omega_2) + \varphi^* (\omega_1 \cap \omega_2)\\ 
  & \le \varphi^* (\omega_1) + \varphi^* (\omega_2)\\
  & \le \lambda_1 + \lambda_2
\end{align*}

Now the proposition follows.

From the Proposition \ref{p2:chap2:sec4:prop5}, we deduce
\begin{coro*}
  If $\{A_i\}$ and $\{a_i\}$ for $i = 1$ to $n$ be two finite family
  of sets such that $a_i \subset A_i$ for every $i$, then any strong
  capacity satisfies: 
  $$
  \varphi^* \left(\bigcup^{n}_{i = 1} A_i\right) + \sum^{n}_{i = 1} \varphi^*
  (a_i) \le \varphi^* \left(\bigcup^{n}_{i = 1} a_i\right) + \sum^{n}_{i = 1}
  \varphi^* (A_i) 
  $$
\end{coro*}

\section{Fundamental Theorem}\label{p2:chap2:sec6} %sect 6

\begin{thm}\label{p2:chap2:sec6:thm2}%theo 2
  If $\varphi$ is a strong capacity on $E, \varphi^*$ is a true
  capacity; and a set is $\varphi^*$- capacitable if and only if the
  inner and outer capacities of the set are equal. 
\end{thm}

\begin{proof} % pro
  The latter assertion is obvious. We have only to prove that
  $\varphi^*$ is a true capacity. 
\end{proof}

The\pageoriginale properties (i) and (iii) of the true capacity have already
been seen for $\varphi^*$. Hence it remains to prove that for any
increasing sequence of sets $A_n, \lim. \varphi^* (A_n) = \varphi^*
(\cup A_n)$. We know the property in the case of open
sets. (Proposition \ref{p2:chap2:sec3:prop1}). Let us now consider the general case. If
$\varphi^* (A_n)$ in $+ \infty $ for any $n$ the result is obvious. We
assume $\varphi(A_n)$ to be finite for every $n$. For $\varepsilon >
0$, we introduce open sets $\omega_n \supset A_n$ such that 
$$
\varphi^* (\omega_n) \le \varphi^* (A_n) + \frac{\varepsilon}{2^n}
$$
for every $n$. We have, by the Proposition \ref{p2:chap2:sec4:prop5}:
\begin{align*}
  \varphi^* \left(\bigcup^{n}_{i = 1} \right)  + \sum^{n}_{i = 1}
  \varphi^* (A_i) 
  & \le \left(\bigcup^{n}_{i = 1} A_i\right) + \sum^{n}_{i = 1} \varphi^*
  (\omega_i)\\ 
  \varphi^* (A_n) & \ge \varphi^* \left(\bigcup^{n}_{i = 1} \omega_i\right) -
  \sum^{n}_{i = 1} \left[ \varphi^*(\omega_i) - \varphi^*
    (A_i)\right]\hspace{2cm}\\  
  & \ge \varphi^* \left(\bigcup^{n}_{i = 1} \omega_i\right) - \sum^{n}_{i = 1}
      \frac{\varepsilon}{2^n}.
      \end{align*}

Hence,
\begin{align*}
\lim\limits_{n \to \infty} \varphi^*
      (A_n) & \ge \varphi^* 
      \left(\bigcup\limits^{\infty}_{i = 1} \omega_i\right) -\varepsilon\\  
      & \ge ^* \left(\bigcup^{\infty}_{i = 1} A_i\right)  - \varepsilon.
\end{align*}

This inequality is true for any arbitrary $\varepsilon > 0$, we get
$\lim\limits_{n \to \infty} \varphi^* (A_n) \ge \varphi^*
\left(\bigcup\limits^{\infty}_{i = 1} A_i\right)$. The other way
inequality being always true\pageoriginale we get the required result. 

\begin{remark*} % rem
  If we suppose that $\varphi$ is just $> -\infty $ (instead of $\ge
  0$) and increasing, continuous to the right and strongly
  subadditive, we may define as well inner and outer capacities, and
  the previous fundamental theorem holds good. The same proofs carry
  over. 
\end{remark*}

\begin{thebibliography}{99}
\bibitem{p2key1}{N. Bourbaki} - Topologie generale, Chap. IX (new edition)

  {}{} Act. Sc. $n^o 1045$
\bibitem{p2key2}{G. Choquet} - Theory of capacities, Annales de l' Institut

  {}{} Fourier t. 5 (1953 - 54)

\noindent
Further researches of : 
\bibitem{p2key3}{Choquet} - Ann. I.f. (1959), Sem potentiel 3 (1959)
\bibitem{p2key4}{Sion} - Trans. Am. S. 96, (1960); ann. I.F. 13, (1963)
\bibitem{p2key5}{Sion and Bressler} - Cand. J. of Math. 16, (1964)
\bibitem{p2key6}{Fuglede} - Acta Math. 103, 1960; Am. I.F. 12, (1962) and
  15-2 (1965) 
\bibitem{p2key7}{Mokobodski} - Sem. Choquet 2, annee 1963
\bibitem{p2key8}{Brelot} - Symp. on prob. (Berkeley 1965)
\end{thebibliography}
