~\phantom{A}
\vfill

\thispagestyle{empty}

\begin{center}
{\huge\bfseries C.~P. Ramanujam}

\vskip 1.5cm

{\Large\bf A Tribute}
\end{center}

\vfill
\eject

~
\thispagestyle{empty}

\vfill\eject


{
~
\thispagestyle{empty}
\vfill

\begin{center}
{\LARGE\bf C.P. RAMANUJAM}\\[15pt]
{\Large\bf --- A Tribute}
\vfill

{\bf Published for the}\\[5pt]
{\large\bf Tata Institute of Fundamental Research}
\vfill

{\Large\bf Springer-Verlag}\\[7pt]
{\bf Berlin ~$\bullet$~ Heidelberg ~$\bullet$~ New York}\\
{\bf 1978}
\end{center}

\vfill\eject

~\phantom{a}
\vfill
\thispagestyle{empty}

\begin{center}
\copyright \; {\bf Tata Institute of Fundamental Research, 1978}\\

\vskip 2cm

\noindent\rule{\textwidth}{1pt}
ISBN  3-540-08770-2--Springer-Verlag.  Berlin -  Heidelberg - 
New York\\
ISBN  0-387-08770-2--Springer-Verlag.  New York - Heidelberg - 
Berlin
\noindent\rule{\textwidth}{1pt}
\vskip .5cm

\begin{center}
\begin{tabular}{p{6.2cm}}
No part of this book may be reproduced in
any form by print, microfilm or any other 
means without written permission from the Tata
Institute of Fundamental Research, Colaba, Bombay 400 005
\end{tabular}
\end{center}

\vskip .5cm

Printed by K.P. Puthran at The Tata Press Limited,\\
414 Veer Savarkar Marg, Bombay 400 025 and Published by H. Goetze\\
Springer-Verlag, Heidelberg, West Germany

\vskip .8cm

Printed In India
\end{center}

\newpage

\thispagestyle{empty}

\begin{center}
{\huge\bf Preface}
\end{center}

\textsc{This collection} of the publications of Chidambaram Padmanabhan 
Ramanujam and of the several papers, in his memory, by his friends and 
colleagues is intended to be a tribute to a distinguished colleague. 

\smallskip

C.P. Ramanujam joined the School of Mathematics of the Tata Institute 
of Fundamental Research as a Research Student in 1957. In his meteoric 
career he had done brilliant work in Number Theory and Algebraic 
Geometry. He was, without doubt, one of the outstanding young Indian 
mathematicians of the last twenty years. Gifted with a remarkably deep 
and wide mathematical culture, he was at home as much with abstract 
Algebraic Geometry as with analytic methods of Number Theory. A 
conversation with him was a rewarding experience for students and 
colleagues alike. He passed away, in Bangalore, when he was hardly 37 
years old. 

\smallskip

I should like to thank all those who contributed papers to this 
volume, and in addition Jal R. Choksi, K. Gowrisankaran, Pavaman 
Murthy, Raghavan Narasimhan and K. Srinivasacharyulu for their 
assistance. I am also grateful to C.P. Rajagopal, brother of 
Ramanujam, for some biographical details concerning Ramanujam. 

\vskip 1cm

\begin{flushright}
\textsc{\bfseries K.G. Ramanathan}
\end{flushright}

\vfill\eject

~\phantom{a}
\thispagestyle{empty}

\vfill\eject

\thispagestyle{empty}
\begin{center}
{\LARGE\bf Acknowledgements}
\end{center}

\bigskip

\textsc{The Editor} and the Tata Institute of Fundamental Research wish to 
thank the following societies and publishers of Journals for kindly 
giving permission to reprint, in this volume, the papers of C.P. 
Ramanujam, as listed below:

\bigskip

\noindent \emph{American Journal of Mathematics:} Johns Hopkins 
University Press, Baltimore

\noindent (No. 7)

\medskip

\noindent \emph{Annals of Mathematics:} the Editors

\noindent (No. 5)

\medskip

\noindent \emph{Journal of the Indian Mathematical Society:} the Editor

\noindent (Nos. 4, 6, 9)

\medskip

\noindent \emph{Mathematika:} University College, London

\noindent (No. 2)

\medskip

\noindent \emph{Mathematische Annalen and Inventiones Mathematicae:} 
Springer-Verlag, Heidelberg

\noindent (Nos. 3, 8, 10)

\medskip

\noindent \emph{Proceedings of the Cambridge Philosophical Society:} Cambridge University Press

\noindent (No. 1)

\newpage

~\phantom{a}
\thispagestyle{empty}

\newpage
}

\thispagestyle{empty}

\noindent
{\bf\huge Contents}

\vskip 1cm
\relax

\noindent
Preface\hfill v
\smallskip

\noindent
Acknowledgements\hfill vii
\smallskip

\noindent
C.P. Ramanujam, by K.G. Ramanathan\hfill 1
\smallskip

\noindent
On Ramanujam's work in algebraic geometry by \hfill 9\;

D. Mumford
\smallskip

\noindent
A note on C.P. Ramanujam, by S. Ramanan\hfill 13
\smallskip

\noindent
Photographs of C.P. Ramanujam\hfill 17-18
\smallskip

\noindent
Facsimile of a page from C.P. Ramanujam's\hfill 19\;

unfinished book on ``Topics in Analysis''

\bigskip

\noindent
{\bf Publications of C.P. Ramanujam}
\vskip -.3cm
\renewcommand{\arraystretch}{1.15}
\begin{longtable}[l]{@{}r>{\raggedright}p{9cm}r}
1. & Cubic forms over algebraic number fields~:\newline
    {\em Proceedings of the Cambridge Philosophical Society,}\newline 59 (1963) 683-705  & 21\\
2. & Sums of $m$-th powers in $p$-adic rings~:\newline
     {\em Mathematika}, 10 (1963), 137-146 & 59\\
3. & A note on automorphism groups of algebraic varieties\newline
    {\em Mathematische Annalen,} 156 (1964), 25-33 & 73\\
4. & On a certain purity theorem~:\newline
     {\em Journal of the Indian Mathematical Society,}\newline 34 (1970), 1-10 & 87\\
5. & A topological characterisation of the affine plane as an algebraic variety~:\newline
{\em Annals of Mathematics,} 94 (1971), 69-88 & 97\\
6. & Remarks on the Kodaira Vanishing Theorem~:\newline
    {\em Journal of the Indian Mathematical Society,}\newline 36 (1972), 41-51 & 123\\
7. & The invariance of Milnor's number implies the invariance of the topological type (jointly with Le Dung Trang)\newline
{\em American Journal of Mathematics,} 98 (1976), 67-78 & 135\\
8. & On a geometric interpretation of multiplicity~:\newline
    {\em Inventiones Mathematicae,} 22 (1973), 63-67 & 151\\
9. & Supplement to the article ``Remarks on the Kodaira Vanishing Theorem''~:\newline 
{\em Journal of the Indian Mathematical Society:}\newline 38 (1974), 121-124 & 159\\
10. & Appendix to the paper of C.S. Seshadri entitled ``Quotient space by an abelian variety''~:\newline 
{\em Mathematische Annalen,} 152 (1963), 192-194 & 165\\
11. & The theorem of Tate, Appendix I to the book entitled ``Abelian Varieties'' by D. Mumford\newline
Tata Institute of Fundamental Research Studies in Mathematics, (1974), 240-260 & 169
\end{longtable}

\medskip

\thispagestyle{empty}

\noindent
{\bf Contributed papers~:}
\vskip -.3cm
\renewcommand{\arraystretch}{1.3}
\begin{longtable}[l]{>{\raggedright}p{9.7cm}r}
\textsc{Le Dung Trang~:} The geometry of the monodromy & 191\\
\textsc{Masayoshi Nagata~:} On Euclid algorithm & 209\\
\textsc{M.S. Raghunathan~:} Principal bundles on affine space & 223\\
\textsc{C.S. Seshadri~:} Geometry of $G/P$---I & 245\\
\textsc{M.V. Nori~:} Varieties with no smooth embeddings & 283\\
\textsc{D. Mumford~:} Some footnotes to the work of C.P. Ramanujam & 289\\
\textsc{S. Raghavan~:} Singular modular forms of degree $s$ & 307\\
\textsc{M. Raynaud~:} Contre-exemple au ``vanishing theorem'' en caract\'eristique $p>0$ & 319\\
\textsc{E. Bombieri} and \textsc{F. Catanese~:} The tricanonical map of a surface with $K^{2}=2$, $p_{g}=0$ & 327\\
\textsc{M.S. Narasimhan} and \textsc{S. Ramanan~:} Geometry of Hecke cycles---I & 341\\
\textsc{B. Teissier~:} On a Minkowski-type inequality for multiplicities---II & 407
\end{longtable}
