\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures On}\\[5pt]
{\Large\bf Some Fixed Point Theorems}\\[5pt]
{\Large\bf Of Functional Analysis}
\vskip 1cm

{\bf By}\\
\medskip

{\large\bf F.F. Bonsall}\\
\vfill

{\bf Tata Institute Of Fundamental Research, Bombay}

{\bf 1962}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures On}\\[5pt]
{\Large\bf Some Fixed Point Theorems}\\[5pt]
{\Large\bf Of Functional Analysis}
\vskip 1cm

{\bf By}\\
\medskip

{\large\bf F.F. Bonsall}\\
\vfill

{\bf Notes by}\\
\medskip

{\large\bf K.B. Vedak}\\
\vfill

\parbox{0.7\textwidth}{No part of this book 
may be reproduced in any form by print, 
microfilm or any other means without written 
permission from the Tata Institute of 
Fundamental Research, Colaba, Bombay 5}
\vfill

{\bf Tata Institute of Fundamental Research}\\

{\bf Bombay}\\

{\bf 1962}
\end{center}
\eject

\thispagestyle{empty}
\chapter*{Introduction}

These lectures do not constitute a systematic account of fixed point
theorems. I have said nothing about these theorems where the interest
is essentially topological, and in particular have nowhere introduced
the important concept of mapping degree. The lectures have been
concerned with the application of a variety of methods to both
non-linear (fixed point) problems and linear (eigenvalue) problems in
infinite dimensional spaces. A wide choice of techniques is available
for linear problems, and I have usually chosen to use those that give
something more than existence theorems, or at least a promise of
something more. That is, I have been interested not merely in
existence theorems, but also in the construction of eigenvectors and
eigenvalues. For this reason, I have chosen elementary rather than
elegant methods.

I would like to draw special attention to the Appendix in which I give
the solution due to B. V. Singbal of a problem that I raised in the
course of the lectures.

I am grateful to Miss K. B. Vedak for preparing these notes and seeing
to their publication. 
\bigskip

\hfill{{\large\bf Frank F. Bonsall}}
