\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf The Finite Element Method}
\vfill

{\bf By}
\medskip

{\large\bf Ph. Ciarlet}
\vfill

{\bf Tata Institute of Fundamental Research}
\medskip

{\bf Bombay}
\medskip

{\bf 1975}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}
\medskip

{\Large\bf The Finite Element Method}
\vfill

{\bf By}
\medskip

{\large\bf Ph. Ciarlet}
\vfill


{\bf Notes by}
\medskip

{\large\bf S. Kesavan, Akhil Ranjan}
\medskip

{\large\bf M. Vanninathan}
\vfill

{\bf Tata Institute of Fundamental Research}
\medskip

{\bf Bombay}
\medskip

{\bf 1975}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
~
\phantom{a}
\vfill

{\bf\copyright \quad Tata Institute of Fundamental Research, 1975}
\bigskip

\parbox{0.7\textwidth}{No part of this book may be reproduced
in any form by print, microfilm or any
other means without written permission
from the Tata Institute of Fundamental
Research, Colaba, Bombay 400005}
\vfill

{\bf Printed In India}
\medskip

{\bf By}
\medskip

{Anil D. Ved At Prabhat Printers, Bombay 400004}
\medskip

{And Published By}
\medskip

{\bf  The Tata Institute of Fundamental Research, Bombay.}
\end{center}
\eject


\chapter{Acknowledgements}


THE AUTHOR EXPRESSES his deep gratitude to Professor Ramana\-than for
his very kind invitation to deliver these lectures at Bangalore, as
part of the T.I.F.R.--I.I.Sc. Mathematics Programme. Also, the author
tanks the T.I.F.R. for financial support.  
\vskip 2cm

\hfill{\large\bf Ph. Ciarlet}



\chapter{Preface}

OUR BASIC AIM has been to present {\em some} of the mathematical
aspects of the finite element method, as well as {\em some}
applications of the finite element method for solving problems in
Elasticity. This is why important topics, such as curved boundaries,
mixed and hybrid methods, time-dependent problems, etc..., are not
covered here. No attempt has been made to give an exhaustive
bibliography. 

