
\begin{thebibliography}{99}

\bibitem{k1} {AGMON S.,\pageoriginale DOUGLIS A., NIRENBERG L.}

  \begin{enumerate}
  \item Estimates near the boundary for solution of elliptic partial
 differential equations satisfying general boundary conditions
 (I). Comm. Pure Applied Math., 12, (1959), pp. 623-727.\label{k1:e1}  
  \end{enumerate}

\bibitem{k2}{AXELSSON 0.}

  \begin{enumerate}
  \item A class of iterative methods for finite element equations,
 Comp. Meth. Appl. Mech. Eng., 19 (1976), pp. 123-138.\label{k2:e1} 
  \end{enumerate}

\bibitem{k3}{BAIOCCHI, C.}

  \begin{enumerate}
  \item Sur un probleme a frontiere libre traduisant le filtrage de
 liquides a travers des milieux poreux. C.R. Acade. Sc. Paris, 273
 A, (1971), pp. 1215 - 1217.\label{k3:e1} 
  \end{enumerate}

\bibitem{k4}{BAUER F., GARABEDIAN P., KORN D. }

  \begin{enumerate}
  \item Superitical wing section (I). Lecture Notes in Economics and
 Math. Systems, Vol. 66, Springer - Verlag, Berlin, 1972.\label{k4:e1}
  \end{enumerate}

\bibitem{k5}{BAUER F., GARABEDIAN P., KORN D., JAMESON A.}

  \begin{enumerate}
  \item Supercritical wing section (II). Lecture Notes in economics
 and Math. Systems Vol. 108, Springer- Verlag, Berlin, 1975. \label{k5:e1}
  \end{enumerate}

\bibitem{k6}{BEGIS D.}

  \begin{enumerate}
  \item  Analyse numerique de  l' ecoulement d'un fluide de
 Bindham. These de 3eme cycle, Universite Pierre et Marie Curie,
 Paris, 1972.\label{k6:e1} 

  \item Etude numerique de l' ecoulement d' un fluide visco-plasique
 de Bingham par une methode de lagrangien augmente. Laboria Report
 355, 1979.\label{k6:e2} 
  \end{enumerate}

\bibitem{k7}{BEGIS D., GLOWINSKI R.}

  \begin{enumerate}
  \item  Chapter 7 of Numerical solution of boundary value problems by
 augmented lagrangians, M. Fortin, R. Gloinski ed. (in
 preparation).\label{k7:e1}
 
  \item  Application de la methode des elements finis a la resolution de
  problemes de domaine optimal. Methods de resolution des problems
  approches. Applied Math. Optimization, 2, (1975), 2, pp. 130-169.\label{k7:e2} 
  \end{enumerate}

\bibitem{k8}{BENSOUSSAN A., LIONS J.L. }

  \begin{enumerate}
  \item Sur l' approximation numerique d' inequations quasi -
 variationnelles statonnaires, in Computing Methods in Applied
 Sciences and Engineering, Part 2, R. Glowinski, J.L. Lions eds.,
 Lecture Notes in Computer Sciences, Vol. 11, Springer - Verlag,
 1974.\label{k8:e1}
  \end{enumerate}

\bibitem{k9}{BENSOUSSAN A., LIONS J.L., TEMAM R.}

  \begin{enumerate}
  \item Sur les methods de decomposition, de decentralisation, de
 coordination et applications. In les Sur Les methods numeriques en
 sciences physiques et eonomiques, J.L. Lions, G. I. Marchouk eds.,
 Dunod- Bordas, Paris, 1974, pp. 133-257.\label{k9:e1} 
  \end{enumerate}

\bibitem{k10}{BERGER A.E}

  \begin{enumerate}
  \item The truncation method for the solution of a class of
 variational inequalities Revue Francaise Automatique, Informaique,
 Rech. Operationnelle, Vol. de, $N^0$ (1956), pp. 29-42.\label{k10:e1} 
  \end{enumerate}

\bibitem{k11}{BERS L.}\pageoriginale

  \begin{enumerate}
  \item Mathematical aspects of subsonic and transonic gas dynamics,
 Chapman and Hall, London, 1958.\label{k11:e1} 
  \end{enumerate}

\bibitem{k12}{BOURGAT J.F., DUVAUT G.}

  \begin{enumerate}
  \item Numerical Analysis of flows with or without wake past a
 symmetric two - dimensional profile, with or without
 incidence. Int. J. Num. Meth. Eng., 11, (1977), pp. 975 - 993.\label{k12:e1} 
  \end{enumerate}

\bibitem{k13}{BRENT R.}

  \begin{enumerate}
  \item  Algorithms for minimization without derivative, Prentice
 Hall, N. J., 1973.\label{k13:e1}
  \end{enumerate}

\bibitem{k14}{BREZIS H}

  \begin{enumerate}
  \item  A new method in the study of subsonic flows. In Partial
 Differential Equations and Related Topics, J. Goldstein ed.,
 Lecture Notes in Math., Vol. 446, Springer - Verlag, Berlin, 1975,
 pp. 50-60.\label{k14:e1} 

  \item Multiplicateur de Lagrange en torsion elasto -
  platique. Arch. Rat. Mech. Anal. 49, (1972), pp. 32-40.\label{k14:e2} 

  \item  Problems unilateraux. J. de Math. Pures et Appliquess 9, Serie
  72, (1971), pp 1-168.\label{k14:e3} 

 \item Monotonicity in Hilbert spaces and some applications to
nonlinear partial differential equations. In Contributions to
Nonlinear Functional Analysis, E. Zarantonello ed., Acad. Press,
New-York, 1971, pp. 101-156.c\label{k14:e4} 

 \item Operateurs maximaux monotones et semmi - groups de contraction
  dans les espaces de Hilbert, North - Holland, Amsterdam, 1973.\label{k14:e5} 
  \end{enumerate}

\bibitem{k15}{BREZIS H., SIBONY M.}

  \begin{enumerate}
  \item  Equivalence de deux inequations variationnelles et
 application Arch. Ract. Mech. Anal. 41, (1971), pp. 254-265.\label{k15:e1} 
  \end{enumerate}

\bibitem{k16}{BREZIS H., STAMPACCHIA G.}

  \begin{enumerate}
  \item  The hodograph method in fluid dynamics in the light of
 variationsl inequalities, Arch, Rat. Mech. Anal. 61, (1976),
 pp. 1-18.\label{k16:e1} 

  \item Sur la regularite de la solution d' inequations
 elliptiques. Bull. Soc. Math. France, 96, (1968),
 pp. 153-180. \label{k16:e2} 
  \end{enumerate}

\bibitem{k17}{BREZIS H., CRANDALL M., PAZY A.}

  \begin{enumerate}
  \item Perturbation of nonlinear monotone sets in Banach
 spaces. Comm. Pure Applied Math., Vol. 23, (1970), pp. 123-144.\label{k17:e1} 
  \end{enumerate}

\bibitem{k18}{BREZZI F., HAGER W.W., RAVIART P.A.}

  \begin{enumerate}
  \item Error estimates for the finite element solution of variational
 inequalities, Part I- Primal Theory. Numer. Math. 28, (1977),
 pp. 431 -443.\label{k18:e1} 
  \end{enumerate}

\bibitem{k19}{BREZZI F., RAVIART P.A.}

  \begin{enumerate}
  \item  Mixed finite element methods for 4th order elliptic
 equations. In Tomos in Numerical Analysis (III), J. J.H. Miller
 ed., Acad, Press, London, 1976, pp. 33-36.\label{k19:e1} 
  \end{enumerate}

\bibitem{k20}{BREZZI F. SACCHI G.}\pageoriginale

  \begin{enumerate}
  \item A finite element approximation of variational inequalities
 related to hydraulics. Calcolo, 13, (1976), pp. 259-273.\label{k20:e1} 
  \end{enumerate}

\bibitem{k21}{BRISTEAU M.O.}

  \begin{enumerate}
  \item  Application de la methode des elements finis a la resoution
 d'inequations variationnnelles d'evolution de type Bingham, These
 de 3ene cycle, Universite Pierre et Marie Curie, Paris, 1975.\label{k21:e1} 

  \item  Applications of optimal control theory to transonic flow
 computations by finite element methods. In Computing methods in
 Applied Sciences and Engineering, 1977, II, R. Glowinski,
 J.L. Lions ed., Lecture Notes in Physics Vol. 91, Springer -
 Verlag, Berlin, 1979, pp. 103 - 124.\label{k21:e2} 
  \end{enumerate}

\bibitem{k22}{BRISTEAU M.O., GLOWINSKI R.}

  \begin{enumerate}
  \item Finite element analysis of the unsteady flow of a viscous -
 plastic fluid in a cylindrical pipe. In Finite Element methods in
 Flow Problems, J. T. Oden, O.C. Zienkiewicz, R. H. Galagher,
 C. Taylor eds., University of Alabama Press, Huntsville, Alabama,
 1974, pp. 471-488.\label{k22:e1} 
  \end{enumerate}

\bibitem{k23}{BRISTEAU M.O., GLOWINSKI R., PERIAUX J., PERRIER P.,
  PIRONNEAU O.} 

  \begin{enumerate}
  \item  On the numerical solution of nonlinear problems in fluid
 dynamics by least squares and finite element methods. (I) Leas
 square formulation and conjugate gradient solution of the
 continuous problem. Comp. Meth. Applied Mech. Eng., 17/18, (1979),
 pp. 619-657.\label{k23:e1}
  \end{enumerate}

\bibitem{k24}{BRISTEAU M.O., GLOWINSKI R., PERIAUX J., PERRIER P., PIRONNEAU 0., POIRIER G.}

  \begin{enumerate}
  \item Applications of optimal control and finite element methods to
 the calculation of transonic flows and incompressible viscous
 flows. Laboria Report 294, (1978), and Numerical methods in
 applied fluid dynamics, B. hunt ed., Acad. Press, London (to
 appear).\label{k24:e1} 

  \item On the numerical solution of nonlinear problem in fluid
 dynamics by least square and finite element methods. (II)
 Application to the computaion of transonic potential flows of
 compressible inviscid fluids (to appear).\label{k24:e2} 
  \end{enumerate}

\bibitem{k25}{CARTAN H.}

  \begin{enumerate}
  \item  Calcul Differentiel. Hermann, Paris, 1967.\label{k25:e1}
  \end{enumerate}

\bibitem{k26}{CEA J., GEYMONAT G.}

  \begin{enumerate}
  \item Une methode de linearisation via 1' optimistion, Instituto di
 Alta Mat. Sym. Mat.m 10, (1972), Bologna, pp. 431 - 451.\label{k26:e1} 
  \end{enumerate}

\bibitem{k27}{CEA J. }

  \begin{enumerate}
  \item Optimization : Theorie et Algorithmes. Dunod, Paris,
    1971.\label{k27:e1} 

  \item  Optimization - Theory and Algorithms. Tata Institute of
 Fundamental Research, Bombay, published by Springer-Verlag,
 Berlin, 1978.\label{k27:e2}
  \end{enumerate}

\bibitem{k28}{CEA J., GLOWINSKI R.}

  \begin{enumerate}
  \item  Sur de methods d' optimisation par relaxation. Revaue
 Francaise Automatique, Informat. Rech. Operationnelle, R-3,
 (1973), pp 53-32.\label{k28:e1} 

  \item Methods numeriques pour 1'ecoulement laminaire d' un fluide
 rigide viscoplatque incompressible. Interm. J. Computer March.,
 Sect. B, Vol. 3, (1972), pp. 225-255.\label{k28:e2}
  \end{enumerate}

\bibitem{k29}{CEA J., GLOWINSKI R., NEDELEC J.C. }\pageoriginale

  \begin{enumerate}
  \item Applications des methods d'optimisation, de differences et d'
 elements finis, a 1' analyse numerique de la torision elasto -
 plastique d' une barre cylindrique. In Approximations et Methods
 Iteratives de Resolution d' Inequations Variationnelles et de
 Problems Non Lineaires. Cahier de 1' IRIA, $N^0$ 12, (1974),
 PP. 7-138.\label{k29:e1} 
  \end{enumerate}

\bibitem{k30}{CHAN T.F., GLOWINSKI R.}

  \begin{enumerate}
  \item Finite element approximation and iterative solution of class
 of midly nonlinear elliptic equations. Stanford University Report
 STAN-CS - 78-674, Comp. Science Department, Stanford University,
 1978.\label{k30:e1} 
  \end{enumerate}

\bibitem{k31}{CIARLET P.G. }

  \begin{enumerate}
  \item The Finite Method, Lecture Notes, Tata Insitute of Fundamental
 Research, Bombay, 1975.\label{k31:e1} 

  \item The Finite Element Method for Elliptic Problems. North
 Holland, Amsterdam, 1978.\label{k31:e2} 

  \item Numerical Analysis of the Finite Element Method. Seminaire de
 Math. Superieures Preses de 1' Universite de Montreal, 1976.\label{k31:e3}
  \end{enumerate}

\bibitem{k32}{CIARLET P.G., RAVIART P. A.}

  \begin{enumerate}
  \item  Interpolation theory over curved elements with applications to
 finite element methods. Comp. Meth. Appl. Mech. Eng., 1, (1972),
 pp. 217 - 249.\label{k32:e1} 

  \item A mixed finite element method for the biharmonic equation. In
 Mathematical aspects of finite element in partial differential
 equation, C. de Boor, ed., Acad. Press, N. Y., 1974, pp. 125 -
 145.\label{k32:e2} 
  \end{enumerate}

\bibitem{k33} {CIARLET P.G., SCHULTZ M.H., VARGA R.S.}

  \begin{enumerate}
  \item Numerical methods of high order accuracy for nonlinear
 boundary value problems. V. Monotone operator theory,
 Numer. Math., 13, (1969), pp, 51-77.\label{k33:e1} 
  \end{enumerate}

\bibitem{k34}{CIARLET P. G., WAGSHAL C.}

  \begin{enumerate}
  \item  Multipoint Taylor Formulas and applications to the Finite
 Element Method. Numerishe Math., Vol. 17, (1971),
 pp. 84-100.\label{k34:e1}  
  \end{enumerate}

\bibitem{k35}{CIAVALDINI J.F., TOUNEMINE G.}

  \begin{enumerate}
  \item A finite element method to compute stationary steady flows in
 the hodograph plane. J. of Indian Math. Soc. 41, (1977),
 pp. 69-82.\label{k35:e1} 
  \end{enumerate}

\bibitem{k36}{CIVALDINI J.F., POGU M., TOURNEMINE G.}

  \begin{enumerate}
  \item Approximation des ecoulements compressibles autour d'un profil
 regulier place en atmoshphere infine: estimation asymptotique
 lorsque 1' on borne le domine exteriur au profile. Rapport de
 l'Universite de Rennes I et de 1' Institut National des Sciences
 Appliquees, March 1979.\label{k36:e1} 

  \item  Une methode variationnelle non lineaire pour 1' etude dans
 plan physique d' ecoulements compressibles subcritiques en
 atmoshphere infinie. Compt. Rend. Acad. Sciences Paris, t. 281 A,
 (1975), pp. 1105 - 1108.\label{k36:e2} 
  \end{enumerate}

\bibitem{k37}{COMINCIOLI V.}

  \begin{enumerate}
  \item On some oblique derivative problems arising in the fluid flow
 in porous media. A theoretical and numerical approach. Applied
 Math. and Optimization, Vol. 1, $N^0$ 4, (1975), p. 313 -336\label{k37:e1} 
  \end{enumerate}

\bibitem{k38}{CONCUS P., GOLUB G.H.}\pageoriginale

  \begin{enumerate}
  \item A generalized conjugate gradient method for non symmetric
 systems of linear equations. In Computing methods in Applied
 Sciences and Engineering, R. Glowinski, J.L. Lions ed., Lecture
 Notes in Economics and Math, Systems, Vol. 134, Springer - Verlag,
 Berlin, 1976, pp. 56-65.\label{k38:e1} 
  \end{enumerate}

\bibitem{k39}{CROUZEIX M.}

  \begin{enumerate}
  \item Sur l' approximation des equations differentielles
 operationnelles par des methodes de Runge-Kutta. These d'Etat,
 Universite Pierre et Marie Curie, Paris, 1975.\label{k39:e1}
  \end{enumerate}

\bibitem{k40}{CRYER C. W.}

  \begin{enumerate}
  \item The method of Christoferson for solving free boundary problems
 for infinite journal bearings by means of finite
 differences. Math. Comp. 25, (1971), pp. 435-443.\label{k40:e1} 
  \end{enumerate}

\bibitem{k41}{DANIEL J.}

  \begin{enumerate}
  \item The approximate minimization of functionals. Prentice Hall,
 N.J., 1970\label{k41:e1} 
  \end{enumerate}

\bibitem{k42}{DUVAUT G., LIONS J.L.}

  \begin{enumerate}
  \item Les inequations en Meanique et en Physique. Dunod, Paris,
 1972.\label{k42:e1}
  \end{enumerate}

\bibitem{k43}{EKELAND I., TEMAM R.}

  \begin{enumerate}
  \item Analyse Convexe et Problemes Variationnels. Dunod - Gauthier -
 Villars, Paris, 1974.\label{k43:e1}
  \end{enumerate}

\bibitem{k44}{FALK R.S.}

  \begin{enumerate}
  \item Approximate solutions of some Variational Inequalities with
 Order of Convergence Estimates. Ph. D. Thesis, Cornell University,
 1971.\label{k44:e1} 

  \item  Error estimates for the approximation of a class of
 Variational Inequalities, Math. Comp., 28, (1974),
 pp. 963-971.\label{k44:e2} 
 
  \item Approximation of an Elliptic Boundary Value Problem with
 Unilateral Constraints Rev. Francaise
 Automat. Informat. Rech. Operationnelle. R2, (1975),
 pp. 5-12.\label{k44:e3}   
  \end{enumerate}

\bibitem{k45}{FALK R.S, MERCIER B.}

  \begin{enumerate}
  \item Error esimate for elasto - plastic problems. Rev. Francaise
 Automat. Informat Rech. Operationnelle, 11, (1977),
 pp. 135-144.\label{k45:e1}  
  \end{enumerate}

\bibitem{k46}{FORTIN M.}

  \begin{enumerate}
  \item Calcul numerique des ecoulements des fluides de Bingham et des
 fluides newtonies incompressibles par des methodes d' elements
 finis. These d'Ettat, Universite Pierre et Marie Curie, Paris,
 1972\label{k46:e1} 

  \item Minimization of some non-differentiable functionals by the
 augment lagrangian method of Hestenes and
 Powell. Appl. Math. Opt., 2, (1976), pp. 236-250.\label{k46:e2} 
  \end{enumerate}

\bibitem{k47}{FORTIN M., GLOWINSKI R.}

  \begin{enumerate}
  \item Chapter 3 of Resolution numerique de problems oux limites par
 des methodes de lagrangien augmente, M. Fortin, R. Glowinski
 ed.(in preparation).\label{k47:e1}

  \item  (Ed.) Resolution numerique de problemes our limites par des
 mithodes de lagrangien augmente, (in preparation).\label{k47:e2} 
  \end{enumerate}

\bibitem{k48}{GABAY D., MERCIER B.}\pageoriginale

  \begin{enumerate}
  \item A dual algorithm for the solution of nonlinear variational
 problems via finite element approximation. Comp. and Math. with
 Applications, Vol. 2, (1976), $N^0$ 1, pp. 17 - 40.\label{k48:e1}
  \end{enumerate}

\bibitem{k49}{GERMAIN P.}

  \begin{enumerate}
  \item Mecanique des MIleux Continus, Vol. 1, Masson, Paris,
 1973.\label{k49:e1}
  \end{enumerate}

\bibitem{k50}{GIRAULT V., RAVIART P.A. }

  \begin{enumerate}
  \item Finite Element Approximation of the Navier- Stokes
 Equations. Lecture Notes in Math., Vol. 749, Springer - Verlag,
 Berlin, 1979.\label{k50:e1} 
  \end{enumerate}

\bibitem{k51}{GLOWINSKI R.}

  \begin{enumerate}
  \item Introduction to the Approximation of Elliptic Variational
 Inequalities. Report 76006, Laboratoire d' Analyse Numerique,
 Universite Pierre et Marie Curie, 1976.\label{k51:e1} 

  \item  Analyse Numereique d' Inequations Variationnelles d'orde
 quatre. Reporf 75002, Laboratoire d' Analyse Numerique, Universite
 Pierre et Marie Curie, 1975.\label{k51:e2} 

  \item Sur 1' approximation d'une inequation variationnelle
 elliptique de type binghan, Revue Francaise d' Automatique,
 Informatique, Recherche Operaionnelle, Vol. 10, 12, (1976),
 pp. 13-30.\label{k51:e3} 

  \item Sur 1' ecoulement d'un fluide de Bingham dans une conduite
 concuite cylidrique. J. de Mecanique, Vol. 1, $N^0$ 4, (1974),
 pp. 601 - 621.\label{k51:e4} 

  \item Numerical Analysis of Nonlinear Boundary Value Problems. (I)
 Methods of Convexity and and Monotonicity (in preparation).\label{k51:e5} 

  \item Approximations externes par elements finis d'ordre un et deux
 du problem de Direchlet pour $\Delta^2$. In Topics in Numerical
 Analysis (I), J. J. H. Miller Ed., Acad. Press, London, 1973,
 pp. 123 - 171.\label{k51:e6}
  \end{enumerate}

\bibitem{k52}{GLOWINSKI R., LANCHON H.}

  \begin{enumerate}
  \item Torsion elasto - plastique d' une barre cylindrique de section
 multiconnexe Journal de Mecanique, 12, (1971), 1, pp. 151
 -171.\label{k52:e1}  
  \end{enumerate}

\bibitem{k53}{GLOWINSKI R., LIONS J.L., TREMOLIERES R.}

  \begin{enumerate}
  \item  Analyse Numerique des Inequations Vaviationnelles, Vol. 1,
 Theorie Generale et Premieres Applications. Dunod - Bordas, Paris,
 1976.\label{k53:e1}  

  \item  Analyse Numerique des Inequations Variationnelles, Vol. 2,
 Applications aux Phenomenes Stationnaires et d' Evolution. Dunod -
 Bordas, Paris, 1976.\label{k53:e2}  

  \item Numerical Analysis of Variational Inequalities, North-Holland,
 Amsterdam (to appear).\label{k53:e3} 
  \end{enumerate}

\bibitem{k54}{GLOWINSKI R., MARROCCO A. }

  \begin{enumerate}
  \item  Analyse Numerique du champ magnetique dans un alternatieur
 tetrapolaire par la methode des elements finis et sur- relaxation
 ponctuelle non lineaire . Comp. Meth. Applied. Mech. Eng., 3,
 (1974), pp. 55-85\label{k54:e1} 

  \item Etude numerique du champ magnetique dans un alternateur
 tetrapolaire par la methoks des elements finis. In Computing
 Methods in Applied Sciences and Engineering, Part 1, R. Glowinski,
 J.L. Lions ed., Lecture Notes in Comp. Sciences, Vol. 10,
 Springer-verlag, Berlin, 1974, pp. 392-409.\label{k54:e2} 

  \item Chapter 5 of Resolution Numerque de Problems aux Limites par
 des Methodes de Lagrangien Augmente, M. Fortin, R. Glowinski eds.,
 (in preparation).\label{k54:e3} 

  \item Sur 1'\pageoriginale approximation par elemets finis d'ordre un et la
 resolution per penalisation-dualite d'nue classe de problems de
 Dirichlet non lineaire. Compt. Rend. Acad.Sc., Paris, t. 278 A,
 (1974), pp (1964-1652)\label{k54:e4} 

  \item On the solution of a class nonlinear Dirichlet problems by a
 penalty- duality method and dinite elemet of order one. In
 Optimization Techmiques : IFIP Technical Conference, G.I.Marchouk
 ed. Lecture Notes in Computer Sciences, Vol.27, Springer-Verlag,
 Berlin, 1975, pp 327-333.\label{k54:e5} 

  \item Sur 1' approximation per elemets finis d'ordre un et la
 resolution par penalisation-dualite, d'une classe de problems de
 Dirichlet non lineaire. Revue Francaise d' Automatique,
 Informatique, Recherche  Operationnelle, Analyse Numerique, R-2
 (1975), pp. 41-76.\label{k54:e6} 

  \item Numerical solution of two dimensional magneto-static problems
 by augmented lagrangian methods. Comp. Meth. Appl. Mech. Eng. ;
 12, (1977), pp. 33-46\label{k54:e7} 

  \item Sur 1' approximation par elements finis order un et la
 resolution par penalistion dualite d'une classe de problems de
 Dirichlet non lineaires, Rapport Laboria 115, 1975 (extended
 version of [6]).\label{k54:e8} 
  \end{enumerate}

\bibitem{k55}{GLOWINSKI R., PIRONNEAU 0.} 

  \begin{enumerate}
  \item On the computation of transonic flows. In Functional Analysis
 and Numerical Anaysis, Japan-France Seminar, Tokyo and Kyoto 1976,
 H.Fujita ed. Japan socity for the Promotion of Science,
 Tokyo,1978, pp. 143-173.\label{k55:e1} 

  \item Numerical methods for the first biharmonic equation and for
 the two-dimensional Stockes problems. SIAM Review, 21, (1979), 2,
 pp. 167-212.\label{k55:e2} 
  \end{enumerate}

\bibitem{k56}{HESTENES M.}
  \begin{enumerate}
  \item  Multiplier and gradient methods. J. Opt.Theoty Appl., 4,
 (1969), pp. 303-320. HEWITT B.L., ILLINGWORTH C.R., LOCK R.C.,
 MANGLER K.W., Mc DONNEL J.H., RICHARDS C., WALKDEN F.\label{k56:e1} 

  \item Computational Methods and problems in Aeronautical Fluid
 Dynamics. Acad. Press, London, 1976.\label{k56:e2} 
  \end{enumerate}

\bibitem{k57}{HOUSEHOLDER A. S.}

  \begin{enumerate}
  \item The numerical treatment of a single nonlinear equation. Mc
 Graw-Hill, N.Y., 1970.\label{k57:e1} 
  \end{enumerate}

 \bibitem{k58}{JAMESON A.}

  \begin{enumerate}
  \item The numerical treatment of a single nonlinear equation. Mc
 Graw-Hill, N.Y., 1970.\label{k58:e1} 
  \end{enumerate}

 \bibitem{k59}{JAMESON A.}
 
  \begin{enumerate}
  \item Transonic flow calulations. In Numerical Methods in Fluid
 Dynamics, H.J.Wirz, J.J Smolderen ed. Mc Graw Hill, N.Y., 1978,
 pp. 1-87.\label{k59:e1} 
 
  \item Three dimensional flows around airfoils with shocks. In
 Computing Methods in Applied Sciences and Engineering (II),
 R. Glowinski, J.L. Lions ed., Lecture Notes in Comp. Sicence,
 Vol.11, Springer -Verlag, Berlin, 1974, pp. 185-212.\label{k59:e2} 
 
  \item Interative solution of transionc flows over airfoils and
 wings, including flows  at Mach 1.Comm. Pure Appl. Math., Vol.27,
 (1974), pp. 283-309.\label{k59:e3} 
 
  \item Numerical solution of nonlinear partial differential equations
 of mixed type. In Numerical solution of Partial Differentail
 Equations-III, Synspads, 1975, B.Habbard ed., Acad.Press, N.Y.,
 1976, pp. 275-320.\label{k59:e4} 
  \end{enumerate}

 \bibitem{k60}{JOHSON C.}\pageoriginale
 
  \begin{enumerate}
  \item A convergence estimate for an approximation of a parabolic
 variational inequality. SIAM J. Num. Anal., 13, (1976), 4,
 pp. 599-606.\label{k60:e1} 
  \end{enumerate}

\bibitem{k61}{KELLOG R.B}
  
  \begin{enumerate}
  \item A nonlinear alternating direction method. Math. of Comp. 23,
 (1969), 105, pp. 23-27.\label{k61:e1}
  \end{enumerate}
 
\bibitem{k62}{KOITER W.T}
  
  \begin{enumerate}
  \item  General Theorems for Flastic Plastic solids. Progress in
 solid mechanics, pp. 165-221. North-Holland, 1960.\label{k62:e1} 
  \end{enumerate}

\bibitem{k63}{LANCHON H.}
  
  \begin{enumerate}
  \item Torsion elasto-plastique d'un arbre cylindrique de section
 simplement ou multiplement connexe. These d' Elat, Universite
 Paris VI, 1972.\label{k63:e1} 
  \end{enumerate}

\bibitem{k64}{LANDHU L., LIFCHITZ E.}
  
  \begin{enumerate}
  \item  Mecanique des Fluides, Mir,Moscow, 1953.\label{k64:e1}
  \end{enumerate}
  
\bibitem{k65}{LASCAUX P.}
  
  \begin{enumerate}
  \item  Numerical methods for time dependent equations.Applications
 to fluid flow problems, lecture Notes, Tata Institute of
 Fundamental Research, Bombay, 1976.\label{k65:e1} 
  \end{enumerate}
  
\bibitem{k66}{LIEUTAUD J.}

  \begin{enumerate}
  \item Approximation d'operateurs par des methods de
 decomposition.These d'Etat, Universite Paris VI, 1968.\label{k66:e1} 
  \end{enumerate}
  
\bibitem{k67}{LIONS J.L}
  
  \begin{enumerate}
  \item Quelques methods se resolution des problems aux limits non
 lineaire. Dunod, Gauthier-Villars, Paris, 1969.\label{k67:e1} 
  
  \item Problems aux limites dans les equations aux derivees
 partielles. Seminaire de Math. Superieures de 1' Universite de
 Montreal. Presses de 1' Universite Montreal, 1962.\label{k67:e2} 
 
  \item Equations differentielles operationnelles et problems aux
 limites. Springer Verlag, 1961.\label{k67:e3} 
 
  \item Controle Optimal des Systemes gouvernes par des equations aux
 derivees partielles. Dunod, Paris, 1968.\label{k67:e4} 
  \end{enumerate}

 \bibitem{k68}{LIONS J.L., MANGENES E.}

  \begin{enumerate}
  \item Problems aux limites nno homogene, Vol, 1. Dunod, Paris,
 1968.\label{k68:e1} 
  \end{enumerate}
 
 \bibitem{k69}{LIONS J.L., STAMPACCHIA G.}
 
  \begin{enumerate}
  \item Variational Inequalities. Comm. Pure Applied Math., XX,
 (1967), pp 493-519.\label{k69:e1} 
  \end{enumerate}
 
 \bibitem{k70}{MORAVETZ C.S.}
 
  \begin{enumerate}
  \item Mixed equations and transonic flows. Rendi Conti di Mat., 25,
 (1960), pp. 1-28\label{k70:e1} 
  \end{enumerate}
 
 \bibitem{k71}{MOSOLOV P.P., MIASNIKOV V.P}\pageoriginale
 
  \begin{enumerate}
  \item  Variational Methods in the Thoey of the Fluidity of a
 Viscous-Plastic Medium. J. Mech. and Appl. Math. (P.M.M),
 Vol.29,(1956), 3,pp. 468-492.\label{k71:e1} 

  \item On stagnant flow regions of a Viscous-Plastic Medium in
 Pipes. J. Mech. and  Appl. Math (P.M.M.), Vol. 30, (1966),
 pp. 705-719.\label{k71:e2} 
 
  \item On qualitative singularities of the flow of a Viscous-Plastic
 Medium in Pipes. J. Mech. and Appl. Math. (P. M. M.), Vol. 31,
 (1967), pp. 581-585.\label{k71:e3} 
  \end{enumerate}

 \bibitem{k72}{MURMAN E.J., COLE J.D.}
 
  \begin{enumerate}
  \item  Calcution of plane steady transonic flows. AIAA Journal,
 Vol. 9, (1971), pp. 114-121.\label{k72:e1} 
  \end{enumerate}

 \bibitem{k73}{NECAS J.}
 
  \begin{enumerate}
  \item Les Methods Directes en Theorie des Equations
 Elliptiques. Masson, Paris, 1967.\label{k73:e1} 
  \end{enumerate}
 
 \bibitem{k74}{ODEN J.T., REDDY J.N}
 
  \begin{enumerate}
  \item Mathematical Theory of Finite Elements. Wiley, N.Y.,
 1976.\label{k74:e1}  
  \end{enumerate}
 
 \bibitem{k75}{OPIAL Z.}
 
  \begin{enumerate}
  \item Weak convergence of the successive approximations for non
 expansive mappings in Banach spaces. Bull. A.M.S., 73, (1967),
 pp. 591-597.\label{k75:e1} 
  \end{enumerate}

 \bibitem{k76}{ORTEGA J., RHEINBOLDT W.C}
 
  \begin{enumerate}
  \item  Iterative solution of nonlinear equations in several
 variables. Acad. Press, N.Y., 1970.\label{k76:e1} 
  \end{enumerate}
 
 \bibitem{k77}{POLAK E.}
 
  \begin{enumerate}
  \item Computational Methods in Optimization. Acad. Press. N.Y.,
 1971.\label{k77:e1}
  \end{enumerate}
 
 \bibitem{k78}{POWELL M.J.D}
 
  \begin{enumerate}
  \item A  method for nonlinear constraints in minimization
 problems. Optimization, R. Fletcher ed., Acad. Press, London,
 1969, Ch. 19. \label{k78:e1}
  \end{enumerate}
 
 \bibitem{k79}{PRAGER W.}
 
  \begin{enumerate}
  \item  Introduction to Mechanics of Continua. Ginn and Company,
 Boston, 1961.\label{k79:e1}
  \end{enumerate}
 
 \bibitem{k80}{RAVIART P.A}
 
  \begin{enumerate}
  \item The use of numerical integration in finite element methods for
 solving parabolic equations. In Topics in Numerical Analysis J.J.H
 Miller ed., Acad. Press, London, 1973, pp., 233-264.\label{k80:e1} 
 
  \item Multistep methods and parabolic equations.In Functional
 Analysis and Numerical Analysis, Japan-France Seminar, Tokyo and
 Kyoto, 1976, H. Fujita ed., Japan Society for the Promotion of
 Science, 1978, pp. 429-454.\label{k80:e2}  
  \end{enumerate}
 
 \bibitem{k81}{ROCKAFELLAR T.R}.
 
  \begin{enumerate}
  \item Convex Analysis. Prinection University Press, Princeton, N.J.,
 1970.\label{k81:e1} 
  \end{enumerate}
 
 \bibitem{k82}{SCHECHTER S.}
 
  \begin{enumerate}
  \item  Iteration methods for nonlinear problems. Trans. Amer,
 Math. Soc., 104, (1962), pp. 601-612.\label{k82:e1} 

  \item Minimization\pageoriginale of Convex Functions by Relaxation ; Ch. 7 of
 Integer and Nonlinear Programming, J. Abadie ed., North - Holland,
 Amsterdam, 1970, pp. 177-189.\label{k82:e2} 

  \item Relaxation methods for convex problems, SIAM J. Num. Anal., 5,
 (1968), pp. 601 -612.\label{k82:e3} 
  \end{enumerate}

\bibitem{k83}{STAMPACCHIA G.}

  \begin{enumerate}
  \item Equations Elliptiques du Second Ordre a Coefficients
 Discontinus. Seminaire de Math. Superieures de 1' Universite de
 Montreal, Presses de 1' Universite de Montreal, 1965.\label{k83:e1} 
  \end{enumerate}

\bibitem{k84}{STRANG G.}

  \begin{enumerate}
  \item  The finte element methof, linear and nonlinear
    applications. {\em Proceedings of the Int. Congress of Math.,
      Vol. 2}, pp 429-436.\label{k84:e1}
  \end{enumerate}

\bibitem{k85}{STRANG G., FIX G.}

  \begin{enumerate}
  \item An  analysis of the finite element method, Prentice Hall,
    N.J., 1973.\label{k85:e1}
  \end{enumerate}

\bibitem{k86}{STRANG G., MOSCO U., }

  \begin{enumerate}
  \item One sided approximation and variational
 inequalities. Bull. American Math. Soc., 80, (1974), pp. 308 -
 312.\label{k86:e1}
  \end{enumerate}

\bibitem{k87}{STRAUSS M.J. }

  \begin{enumerate}
  \item Variations of Korn's and Sobolev's Inequalities. In
 Proceedings of Symposia in Pure Math., Vol. 23, A.M.S.,
 Providence, R. I., 1973, pp. 207 - 214.\label{k87:e1} 
  \end{enumerate}

\bibitem{k88}{TEMAM R.}

  \begin{enumerate}
  \item Navier - Stokes equations. North - Holland, Amsterdam,
 1977.\label{k88:e1}
  \end{enumerate}

\bibitem{k89}{TREMOLIERES R.}

  \begin{enumerate}
  \item Inequations Variationnelles : Existence, Approximations,
 Resolution. These d'Etat. Universite Pierre et Marie Curie, Paris,
 1972.\label{k89:e1} 
  \end{enumerate}

\bibitem{k90}{VARGA R.S.}

  \begin{enumerate}
  \item Matrix Iterative Analysis, Prentice-Hall, N.J.,
 1962.\label{k90:e1}
  \end{enumerate}

\bibitem{k91}{YOSIDA K.}

  \begin{enumerate}
  \item Fuctional Analysis, Springer-Verlag, Berin, 1965.\label{k91:e1}
  \end{enumerate}

\bibitem{k92}{YOUNG D.M.}

  \begin{enumerate}
  \item {Itarative solution of Large Linear Systems. Acad. Press,
 New-York, 1971.}\label{k92:e1}
  \end{enumerate}
\end{thebibliography}

