~\vfill

\begin{center}
{\Large\bf Vector Bundles On}
\medskip

\thispagestyle{empty}

{\Large\bf Algebraic Varieties}
\end{center}

\vfill\eject

~\phantom{a}
\thispagestyle{empty}

\vfill\eject


\thispagestyle{empty}

~
\vfill

\begin{center}
{\Large\bf VECTOR BUNDLES ON}
\medskip

\thispagestyle{empty}

{\Large\bf ALGEBRAIC VARIETIES}
\end{center}

\vskip 1cm

Papers presented at the Bombay Colloquium 1984, by

\smallskip

\begin{center}
ATIYAH AYOUB BARTH BHATWADEKAR

COLLIOT-TH\'EL\`ENE DREZET HIRSCHOWITZ

HORROCKS HULEK KEMPF KNUS LE POTIER

LINDEL MARUYAMA MOORE MUKAI

NARASIMHAN OJANGUREN PARIMALA

RAMANAN RAMANATHAN SESHADRI

SRIDHARAN SRINIVAS TRAUTMANN

\vfill

{\bf\em Published for the}
\medskip

{\large\bf TATA INSTITUTE OF FUNDAMENTAL RESEARCH, BOMBAY}

\medskip

{\large\bf OXFORD UNIVERSITY PRESS}

\smallskip

{\bf BOMBAY DELHI CALCUTTA MADRAS}

{\bf 1987}
\end{center}


\newpage

~\phantom{a}
\vfill

\thispagestyle{empty}


\begin{center}
{\em Oxford University Press, Walton Street, Oxford OX2 6DP}
\medskip

NEW YORK TORONTO

DELHI BOMBAY CALCUTTA MADRAS KARACHI

PETALINGJAYA SINGAPORE HONGKONG TOKYO

NAIROBI DAR ES SALAAM

MELBOURNE AUCKLAND

\bigskip

and associates in
\smallskip

BEIRUT BERLIN IBADAN NICOSIA


\vskip 1cm

\copyright\ Tata Institute of Fundamental Research, 1987

\vfill

Printed in India by K. M. Aarif,

Paper Print India, Worli, Bombay 400018

and published by R. Dayal, Oxford University Press

Oxford House, Apollo Bunder, Bombay 400039
\end{center}

\eject

\thispagestyle{empty}

\noindent
{\bf\huge Contents}

\vskip 1cm


\noindent
\renewcommand{\arraystretch}{1.7}
\begin{longtable}[l]{r>{\raggedright}p{9cm}r}
1. & M.F. Atiyah~: Magnetic monopoles in hyperbolic spaces & 1\\
2. & W. Barth, K. Hulek and R. Moore~: Shioda's modular surface
$S(5)$ and the Horrocks-Mumford bundle & 29\\
3. & S.M. Bhatwadekar~: Some results on a question of Quillen & 79\\
4. & J.-L. Colliot Th\'el\`ene~: A problem of Zariski & 93\\
5. & J.M. Drezet and J. Le Potier~: Conditions d'existence des fibres
stables de rang \'elev\'e sur $\mathbb{P}^{2}$ & 97\\
6. &  A. Hirschowitz~: Rank techniques and jump stratifications & 115\\
7. & G. Horrocks~: Vector bundles on the punctured spectrum of a
local ring II & 155\\
8. & G.R. Kempf~: Some metrics on Picard bundles & 165\\
9. &  M.-A. Kuns~: Bundles on $\mathbb{P}^{2}$ with a quaternionic
structure & 173\\
10. &  H. Lindel~: On projective modules over positively graded rings
& 195\\
11. & M. Maruyama~: Vector bundles on $\mathbb{P}^{2}$ and torsion
sheaves on the dual plane & 213\\
12. & S. Mukai~: On the moduli space of bundles on $K3$ surfaces, I & 263\\
13. & M.S. Narasimhan and S. Ramanan~: $2\theta$-linear systems on
abelian varieties & 315\\
14. & M.S. Narasimhan and G. Trautmann~: Compactification of $M(0,2)$
& 325\\
15. & M. Ojanguren and G. Ayoub~: The Witt group of a real surface & 337\\
16. &  M. Ojanguren, R. Parimala and R. Sridharan~: Anisotropic
quadratic spaces over the plane & 353\\
17. & A. Ramanathan~: Unitary bundles and restrictions of stable
sheaves & 373\\
18. & C.S. Seshadri~: Line bundles on Schubert varieties & 379\\
19. & V. Srinivas~: Zero cycles on a singular surface~: an
introduction & 401\\
\end{longtable}

\thispagestyle{empty}


