\thispagestyle{empty}
\vfill
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Topics In Finite Element Solution of}\\[5pt]
{\Large\bf Elliptic Problems}
\vfill

{\bf By}\\[5pt]
{\large\bf Bertrand Mercier}
\vfill

{\bf Tata Institute of Fundamental Research}

{\bf Bombay}

{\bf 1979}
\end{center}

\eject

\thispagestyle{empty}

\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Topics In Finite Element Solution of}\\[5pt]
{\Large\bf Elliptic Problems}
\vfill

{\bf By}\\[5pt]
{\large\bf Bertrand Mercier}
\vfill

{\bf Notes By}\\[5pt]
{\large\bf G. Vijayasundaram}
\vfill

{Published for the}\\[5pt]
{\bf Tata Institute of Fundamental Research, Bombay}
\vfill

{Springer-Verlag}\\
{Berlin Heidelberg New York}\\
{\bf 1979}
\end{center}

\eject

\thispagestyle{empty}

\begin{center}
{\Large\bf Author}\\[6pt]
{\large\bf Bertrand Mercier}\\
{Ecole Polytechnique\\
Centre de Mathematiques Appliquees\\
91128 Palaiseau (France)}
\vfill

{\bf\copyright\quad  Tata Institute of Fundamental Research, 1979}\\
\medskip

\noindent\rule{\textwidth}{1pt}

ISBN  3--540--09543--8  Springer-Verlag  Berlin.  Heidelberg. New York\\

ISBN  0--387--09543--8  Springer-Verlag  New York  Heidelberg. Berlin

\noindent\rule{\textwidth}{1pt}
\vfill

\parbox{0.7\textwidth}{No part of this book may be reproduced in any form
by print, microfilm or any other means without 
written permission from the Tata Institute of 
Fundamental Research, Bombay 400 005}
\vfill

Printed by N.S. Ray at The Book Centre Limited,\\
Sion East, Bombay 400 022 and published by H. Goetze\\
Springer-Verlag, Heidelberg, West Germany
\vskip .5cm

Printed In India
\end{center}


\chapter{Preface}
\markboth{Preface}{Preface}


THESE NOTES SUMMARISE a course on the finite element solution of
Elliptic problems, which took place in August 1978, in Bangalore.

I would like to thank Professor Ramanathan without whom this course
would not have been possible, and Dr. K. Balagangadharan who welcomed
me in Bangalore.

Mr. Vijayasundaram wrote these notes and gave them a much better form
that what I would have been able to.

Finally, I am grateful to all the people I met in Bangalore since they
helped me to discover the smile of India and the depth of Indian
civilization.
\bigskip

\begin{flushright}
{\large\bf Bertrand Mercier}\\
Paris, June 7, 1979.
\end{flushright}

