\chapter{Lecture 8}

\begin{proposition}%propo 4
 If\pageoriginale $\sum' \xrightarrow{g} \sum \xrightarrow{f} \sum''$ is an
  exact sequence of homomorphisms of presheaves, i.e. if each
  sequence 
$$
(A_U, S'_U) \xrightarrow{g_{_U}} (A_U , S_U) \xrightarrow{f_U} (A_U,
  S''_U) 
$$
is exact, then the induced sequence $\mathscr{S}' \xrightarrow{g} 
\mathscr{S} \xrightarrow{f}\mathscr{S}''$ of sheaves is also exact. 
\end{proposition}

\begin{proof}
The sequences $(A_x, S'_x) \to (A_x, S_x) \to (A_x, S''_x)$ are exact
by a property of the direct limit. 
\end{proof}

\textit{Induced homomorphism of presheaves of sections}. If
$\mathscr{S}'$, $\mathscr{S}$ are sheaves of $\mathfrak{a}$-modules and $g :
\mathscr{S}' \to \mathscr{S}$ is a homomorphism, there is a
homomorphism $\bar{g} : \bar{\mathscr{S}'} \to \bar{\mathscr{S}}$ of
the presheaves of sections with $\bar{g}_U : \Gamma (U,\mathscr{S}')
\to \Gamma (U,\mathscr{S})$ defined by $\bar{g}_U(f) = gf$. This
homomorphism takes all sections through $s' \in S'$ into sections
through $g s'$. Thus, with the usual identification, $\bar{g}$ inducts
the sheaf homomorphism $g:s'\to s$.

\noindent
\textit{Quotient Sheaves.} 

\begin{proposition}%propo 5
If $\mathscr{S}$ is a sheaf of $a$-modules and $\mathscr{S}'$ is
  a subsheaf of $\mathscr{S}$, there is a unique sheaf
  $\mathscr{S}''$, whose stalks are the quotient modules $S''_x =
S_x/S'_x$, such that $j : \mathscr{S} \to \mathscr{S}''$ where
  $j|S_x = j_x : S_x \to S''_x$ is the natural homomorphism, is a
  sheaf homomorphism. 

$\mathscr{S}''$ is the quotient sheaf $\mathscr{S}''
  =\mathscr{S}/ \mathscr{S}'$. 
\end{proposition}

\begin{proof}
If\pageoriginale $S'' = \bigcup_x S_x / S'_x$ is to have a topology such that $j :
\mathscr{S} \to \mathscr{S}''$ is a sheaf homomorphism, $S''$ must be
covered by sections which are image $jf(U)$ of sections of
$\mathscr{S}$, and this uniquely determines the topology of
$S''$. This topology has the property that a set $V$ of $S''$ is open
if and only if $j^{-1}V$ is open. Thus $\mathscr{S}''$ if it exists,
is unique. 
\end{proof}

$\Gamma (U, \mathscr{S}')$ is a sub-$\Gamma (U, \mathfrak{a})$-module
of $\Gamma (U, \mathscr{S})$ and let $\phi_{VU}| \Gamma (U,
\mathscr{S}')\break = \phi'_{VU}$. Let $S''_U = \Gamma (U,\mathscr{S})/ \Gamma (U,
\mathscr{S}')$ and let $j_U : \Gamma (U, \mathscr{S}) \to S''_U$ be
the natural homomorphism. Let $\phi_{VU}'' : S''_U \to S''_V $ denote
the homomorphism induced by $\phi_{VU}$. Then 
$\sum''=\{A_U, S''_U, \phi''_{VU}\}$ is a presheaf and the sequence $0
\to (\bar{\mathfrak{a}}, \bar{\mathscr{S}')}\xrightarrow{f}
(\bar{\mathfrak{a}}, \bar{\mathscr{S}})\xrightarrow{j} \sum'' \to 0$
is exact, where 0 is the presheaf $\{A_U, 0_U, \ldots\}$. Then the
induced sequence of sheaves  
$$
0 \to \mathscr{S}' \xrightarrow{i} \mathscr{S} \xrightarrow{i}
\mathscr{S}'' \to 0, 
$$
where $\mathscr{S}''$ is the sheaf determined by $\sum''$, is
exact. That is, for each $x$, the sequence 
$$
0 \to S'_x \xrightarrow{i_x} S_x \xrightarrow{j_x} S''_x \to 0
$$
is exact. Thus $j_x$ induces an isomorphism $S_x /S'_x \to S''_x$, and
if we identify $S''_x$ with $S_x / S'_x$, $j_x : S_x \to S_x/S'_x$ is
the natural homomorphism. Thus a sheaf $\mathscr{S}''$ having the
required properties exists. 

\begin{defi*}
{\em A homomorphism} $f : (\mathfrak{a},\mathscr{S}) \to (\mathscr{B},
\mathscr{R})$ consists of maps $f' : A \to B$ and  and $f'' : S \to
R$, commuting with the projections, such\pageoriginale that the
restrictions $f'_x = 
f' | A_x \to B_x$ and $f''_x = f'' |S_x: S_x \to R_x$ give a
homomorphism $f_x = (f'_x, f''_x) : (A_x, S_x) \to (B_x, R_x)$. 
\end{defi*}

\textit{If $f : (a, \mathscr{S}) \to (\mathcal{B}, \mathbb{R})$ is a
  sheaf homomorphism and if $\mathscr{S}'$, $\mathscr{R}'$ are subsheaves
  of $\mathscr{S}$, $\mathscr{R}$ respectively such that $f(S') \subset
  R'$, there are induced homomorphisms 
$$
f' : (a, \mathscr{S}') \to (\mathscr{B}, \mathscr{R}'),~f'' : (a,
\mathscr{S}/\mathscr{S}') \to (\mathscr{B}, \mathscr{R}/_\mathscr{R}') 
$$
with $f i = i f'$, $f'' j = jf$, where $i$ denotes the inclusion
homomorphism and $j$ the natural homomorphism of a sheaf onto a
quotient sheaf.} 

\begin{proof}
The result is clear for stalks, and the fact that $f'$, $f''$ are
homomorphisms follows from the fact they are continuous. 
\end{proof}

\begin{exam}%them 13.
Let $X$ be the circle $|z|=1$, let $\mathscr{S}$ be the constant sheaf
$(X \times Z, \pi, X)$ of integers over $X$ and let $\mathscr{S}'$ be
the subsheaf obtained by omitting the points $(1, n)$ for $n \neq
o$. Then $\mathscr{S}/\mathscr{S}'$ is isomorphic to the sheaf of
Example 4. 
\end{exam}

\begin{exam}%them 14.
Let $X$ be the complex plane. Let $S_U$ be the additive abelian group
of functions analytic in $U$, let $S''_U$ be the multiplicative
abelian group of non-vanishing analytic functions in $U$ and let $j_U
: S_U \to S''_U$ be the homomorphism defined by $j_Uf = e^{2 \pi 
  if}$. The system $\{j_U\}$ gives a homomorphism of presheaves and
there is an induced exact sequence of sheaves  
$$
0 \to Z \to \mathscr{S} \to \mathscr{S}'' \to 0
$$
where\pageoriginale $Z$ is the constant sheaf of integers. An element
of $\Gamma (X, \mathscr{S})$ is a function analytic in the whole
plane.  
\end{exam}

More generally, in this example $X$ can be replaced by a complex
analytic manifold. 

\medskip
\noindent
\textbf{Tensor products of sheaves.} 

Let $a$, $\mathscr{B}$ be sheaves of \textit{commutative rings with unit
  element} let $\mathscr{R}$, $\mathscr{S}$ be sheaves of
$\mathfrak{a}$-modules and let $\mathcal{J}$ be a sheaf of
$\mathscr{B}$-modules.  

\begin{defi*}
A {\em bihomomorphism} $f : (\mathfrak{a} ,\mathscr{R},\mathscr{S}) \to
(\mathscr{B}, \mathcal{J})$ consists of maps $f' : A \to B$, $f'' : R +
S \to T$, which commute with the projections, such that, for each $x
\in X$, the restriction $f_x : (A_x, R_x, S_x) \to (B_x, T_x)$ is a
bihomomorphism. 
\end{defi*}

If $r \in \Gamma (U, \mathscr{R})$, $s \in \Gamma(U,
\mathscr{S})$ there is a section $t : U \to T$ defined by $t(x) = f''
( r(x), s(x))$. That $t$ is a map follows from the fact that it is the
composite of the two maps  
$$
U = U + U \xrightarrow{r, s} R+S \xrightarrow{f''} T ; 
$$
where $U+U$ is the set of points $(x,x)$, $x \in U$. We write $t=f''_U
(r,s)$. Then $f_U : (A_U, R_U, S_U) \to (B_U, T_U)$ where $A_U =
\Gamma (U, \mathfrak{a})$, etc., is a bihomomorphism, as follows from
the property at each $x$, $e.g$.  
\begin{align*}
f''_U (ar, s)(x) & = f''((ar)(x), s(x)) = f''(a(x) r(x), s(x)\\
& = f'(a(x)). f''(r(x), s(x)) = (f'_U(a))(x). f''_U(r,s)(x)\\
& = (f'_U(a). f''_U (r,s)) (x),
\end{align*}
and similarly the other properties can be proved. Clearly $f_U$
commutes with\pageoriginale the restriction of functions; $f_V
\phi_{VU}= \theta_{VU} f_U$.  
\[
\xymatrix{
(A_U, R_U, S_U) \ar[r]^{f_U} \ar[d]_{\phi_{VU}} & (B_U,
  T_U)\ar[d]_{\theta_{VU}}\\
(A_V, R_V, S_V) \ar[r]_{f_V} \ar[d]_{\phi_{xV}} & (B_V,
  T_V)\ar[d]_{\theta_{xV}}\\
(A_x, R_x,S_x) \ar[r]_{f_x} & (B_x,T_x)
}
\]


Also $f_x \phi_{xU}(r, s) = f(r (x), s(x)) = f_U(r, s) (x) =
\theta_{xU}f_u (r, s)$; i.e., $f_x \phi_{xU} = \theta_{xU}
f_U$. Thus the bihomomorphism $f$ is determined by the system of
bihomomorphisms $\{f_U \}$. 

\begin{proposition}%propo 6.
 If $\mathfrak{a}$ is a sheaf of commutative rings with unit, and
  $\mathscr{R}$, $\mathscr{S}$ are sheaves of $\mathfrak{a}$-modules,
 there exists a sheaf $\mathscr{Q}$ of $\mathfrak{a}$-modules and a
 bihomomorphism $\alpha : 
  (\mathscr{R},\mathscr{S}) \to \mathscr{Q}$ with im $\alpha_x$
  generating $Q_x$ for each $x$, such that if $f: (\mathfrak{a},
  \mathscr{R},\mathscr{S}) \to (\mathscr{B},\mathscr{J})$ is any
  bihomomorphism there is a (unique) homomorphism $\bar{f}: (\mathfrak{a},
  \mathscr{Q}) \to (\mathscr{B}, \mathscr{J})$ with $\bar{f}. \alpha =
  f$. The sheaf $\mathscr{Q}$ together with the bihomomorphism $\alpha$
  is called the tensor product $\mathscr{R} \otimes_{\mathfrak{a}}
  \mathscr{S}$ and is unique upto isomorphism. Each $Q_x$ together
  with $\alpha_x :   (R_x, S_x) \to Q_x$ is the tensor product $R_x
  \otimes_{A_x}S_x$. The sections $q(U)$ where $q(x)= \sum^k_{i=1}
  \alpha_x (r_i (x)$, $s_i(x))$ with $r_i \in \Gamma (U, a)$, $s_i
  \in \Gamma (U,\mathscr{S})$ and $o < k < \infty$, form a base for
  the open sets of $\Omega = \bigcup_x Q_x = \bigcup_x R_x
  \otimes_{A_x} S_x$. 
\end{proposition}

\begin{proof}
Let\pageoriginale $\{A_U, R_U, S_U, \phi_{VU}\}$ be the presheaf
$(\bar{\mathfrak{a}}, 
\bar{\mathscr{R}}, \bar{\mathscr{S}})$ i.e., $A_U =\break \Gamma (U,\mathfrak{a})$,
etc. For each $\phi_{VU}, \phi_{VU}: (A_U, R_U, S_U) \to (A_V, R_V,
S_V)$ there is an induced homomorphism $\bar{\phi}_{VU}: (A_U, R_U
\otimes_{A_U}S_U) \to (A_V, R_V \otimes_{A_V}S_V)$ and the system
$\bigg\{A_U, R_U \otimes_{A_U} S_U, \bar{\phi}_{VU}\bigg\}$ is a
presheaf determining some sheaf $(\mathfrak{a},\mathscr{Q})$. 
\end{proof}

Since tensor products and direct limits commute, for each $x$, there
is a unique induced bihomomorphism $\alpha_x : (R_x, S_x) \to Q_x$
with $\alpha_x \phi_{xU}= \bar{\phi}_{xU} \alpha_U$ and $Q_x$
together with $\alpha_x$ is the tensor product $R_x \otimes_{A_x}
S_x$. An arbitrary element $q= \sum^k_{i=1} \alpha_U (r_i, s_i) \in
R_U \otimes_{A_U} S_U$ determines a section $q_U : U \to \Omega$ where 
\begin{align*}
q_U (x)=\bar{\phi}_{xU} q & = \sum^k_{i=1} \bar{\phi}_{xU} \alpha_U
(r_i, s_i) = \sum^k_{i=1} \alpha_x \phi_{xU}(r_i, s_i)\\ 
& = \sum^k_{i=1} \alpha_x (r_i (x), s_i(x)) 
\end{align*}
and such sections from a base for $Q$.

If $f: (\mathfrak{a}, \mathscr{R}, \mathscr{S}) \to (\mathscr{B},
\mathscr{J})$ is 
any bihomomorphism, there is an induced homomorphism $\{f_U\}: 
(\bar{\mathfrak{a}}, \bar{\mathscr{R}}, \bar{\mathscr{S}}) \to
(\bar{\mathscr{B}}, \bar{\mathscr{J}})$ of presheaves. Then, if
$\bar{f}_U : (A_U, R_U \otimes_{A_U}S_U) \to (B_U, T_U)$ is the
homomorphism induced by $f_U$, 

$\bigg\{ \bar{f}_U \bigg \}:\bigg \{A_U, R_U \otimes_{A_U} S_U,
\phi_{VU}\bigg\} \to \bigg\{\bar{\mathscr{B}}, \bar{\mathscr{J}}
\bigg\}$ is a homomorphism of presheaves which induces a homomorphism
$\bar{f}: (\mathfrak{a}, \mathscr{Q}) \to (\mathscr{B}, \mathscr{J})$ of
sheaves. Then 
{\fontsize{10}{12}\selectfont
\[
\xymatrix{
& (A_U, R_U, S_U)\ar[r]^{\phi_{VU}} \ar[d]_{\alpha_U}
  \ar@{-}[dl] & (A_V, R_V, S_V) \ar[r]^{\phi_{xV}}
  \ar[d]_{\alpha_V} \ar@{-}[dr]^{f_V} & (A_x, R_x,
  S_x)\ar@{-}[dr]^{f_x}\ar[d]_{\alpha_x}\\
\ar[dr] & (A_U, R_U \otimes_{A_U} S_U) \ar[r]^{\phi_{VU}}
\ar[d]_{\bar{f_U}} & (A_V, R_V \otimes_{A_V} S_V) \ar[d]_{\bar{f}_V}
\ar[r]^{\phi_{xV}} & (A_x,Q_x) \ar[d]_{\bar{f}_x} \ar[dl] & \ar[dl]\\
& (B_U, T_U) \ar[r]^{\theta_{VU}} & (B_V,T_V) \ar[r]^{\theta_{xV}} &
(B_x, T_x)
}
\]}\relax\pageoriginale
$$
\bar{f}_x \alpha_x \phi_{xU}(r, s) = \theta_{xU}\bar{f}_U \alpha_U(r,
s) = \theta_{xU} f_U(r, s) = f_x \phi_{xU}(r,s) ; 
$$
thus $\bar{f}_x \alpha_x = f_x$ and hence $\bar{f} \cdot \alpha = f$. Since
im$\alpha_x$ generates $R_x \otimes_{A_x} S_x = Q_x$, $\bar{f}_x$ is
uniquely determined by $f_x$; hence $\bar{f}$ is unique. That
$\mathcal{Q}$ and $\alpha$ are unique upto isomorphism is proved in
the usual manner. 

\begin{coro*}%Corlry
If $\phi : (\mathfrak{a}, \mathscr{R}, \mathfrak{S}) \rightarrow
(\mathscr{B}, \mathfrak{J}, \mathcal{U})$ is a homomorphism, there is
a unique induced homomorphism $\bar{\phi} : (\mathfrak{a},
\mathscr{R}\otimes_{\mathfrak{a}} \mathscr{S}) \rightarrow
(\mathscr{B}, \mathfrak{J} \otimes_{\mathscr{B}}\mathcal{U}) $ with
$\bar{\phi} \alpha = \beta \phi$ 
\[
\xymatrix{
(\mathfrak{a}, \mathscr{R}, \mathscr{s}) \ar[d]_{\phi}
  \ar[r]^{\phi} & (\mathscr{B}, \mathfrak{J},
  \mathcal{U})\ar[d]^{\beta}\\
(\mathfrak{a}, \mathscr{R} \otimes_{\mathfrak{a}} \mathscr{S}
  \ar[r]^{\bar{\phi}} & (\mathscr{B}, \mathfrak{J} \otimes_{\beta}
  \mathcal{U}), 
}
\]
\end{coro*}


