\title{International Colloquium on Vector Bundles on Algebraic
  Varieties\break
{\fontsize{13}{15}\selectfont Bombay, 9-16 January 1984}}

\author{REPORT}
\date{}
\maketitle

\thispagestyle{empty}

AN INTERNATIONAL  COLLOQUIUM on `Vector Bundles on Algebraic Varieties'
was held at the Tata Institute of Fundamental Research, Bombay from
January 9 to January 16, 1984. The purpose of the Colloquium was to
highlight recent developments in the general area of Vector Bundles as
well as principal bundles on both affine and projective
varieties. Projective modules and quadratic spaces over general rings
were also among the topics covered by the Colloquium. The Colloquium
was jointly sponsored by the International Mathematical Union and the
Tata Institute of Fundamental Research, and was financially supported
by them and the Sir Dorabji Tata Trust.

The Organizing Committee for the Colloquium consisted of Professors
Sir M.F. Atiyah, M.P. Murthy, M.S. Narasimhan, M.S. Raghunathan,
S. Ramanan and R. Sridharan. The International Mathematical Union was
represented by Professors Atiyah and Narasimhan

The following mathematicians gave one-hour addresses at the
Colloquium~:

\smallskip
\noindent
M.F. Atiyah, W. Barth, S.M. Bhatwadekar, J.L. Colliot-Th\'el\`ene,
A. Hirschowitz, G. Horrocks, G.R. Kempf, M.A. Knus, J. Le Potier,
H. Lindel, M. Maruyama, N. Mohan Kumar, S. Mukai, M. Ojanguren,
R. Parimala, S. Ramanan, A. Ramanathan, C.S. Seshadri, V. Srinivas and
G. Trautmann.

\newpage

\noindent
Besides the members of the School of Mathematics of the Tata
Institute, mathematicians from universities and educational
institutions in India and France were also invited to attend the
Colloquium.

\smallskip
\noindent
The social programme for the Colloquium included a Tea Party on
January 9, a Classical Indian Dance (Bharata Natyam) Performance on
January 10, a Concert (Classical Indian Music) on January 12, a Dinner
Party at the Institute on January 13, an Excursion to Elephanta Caves
on January 14, a Film Show on January 15, and a Farewell Dinner Party
on January 16, 1984. 

\lhead[]{}
\markboth{REPORT}{}

