\chapter{Second South Asian Conference on Mathematical Education}

\begin{center}
{\bf BOMBAY, 20-27 JANUARY 1960}
\medskip

{\large\bf LIST OF PARTICIPANTS}
\end{center}

\setcounter{pageoriginal}{202}
\pageoriginale
\renewcommand{\arraystretch}{1.2}
\begin{longtable}{r@{\;\,}ll}
1. & Dr. \textsc{J. P. Agarwal} & (India)\\
2. & Professor \textsc{D. S. Agashe} & (India)\\
3. & Professor \textsc{Y. Akizuki} & (Japan)\\
4. & Professor \textsc{A. D. Alexandrov} & (U.S.S.R.)\\
5. & Professor \textsc{Emil Artin} & (W. Germany)\\
6. & Professor \textsc{W. L. Baily} & (U.S.A.)\\
7. & Professor \textsc{T. J. Balwani} & (India)\\
8. & Professor \textsc{Ram Behari} & (India)\\
9. & Professor \textsc{Lipman Bers} & (U.S.A.)\\
10. & Dr. \textsc{H. J. Bhabha} & (India)\\
11. & Professor \textsc{T. A. A. Broadbent} & (U.K.)\\
12. & Professor \textsc{H. Cartan} & (France)\\
13. & Professor \textsc{K. Chandrasekharan} & (India)\\
14. & Dr. \textsc{L. M. Chawala} & (Pakistan)\\
15. & Dr. \textsc{J. R. Choksi} & (India)\\
16. & Mr. \textsc{R. M. de Cruz} & (Singapore)\\
17. & Professor \textsc{C. J. Eliezer} & (Malaya and Singapore)\\
18. & Professor \textsc{W. Fenchel} & (Denmark)\\
19. & Professor \textsc{B. V. Gnedenko}\footnote{Did not attend the conference} & (U.S.S.R.)\\
20. & Mr. \textsc{K. N. Gowrisankaran} & (India)\\
21. & Professor \textsc{H. Grauert} & (W. Germany)\\
22. & Dr. \textsc{K. B. Gundlach} & (W. Germany)\\
23. & Professor \textsc{K. R. Gunjikar} & (India)\\
24. & Dr. \textsc{Syed Qasim Husain} & (Pakistan)\\
25. & Professor \textsc{V. S. Huzurbazar} & (India)\\
26. & Professor \textsc{R. Kawai} & (Japan)\\
27. & Professor \textsc{V. S. Krishnan} & (India)\\
28. & Professor \textsc{Wolfgang Krull} & (W. Germany)\\
29. & Professor \textsc{M. Kuranishi} & (Japan)\\
30. & Professor \textsc{A. Lichnerowicz} & (France)\\
31. & Miss \textsc{Chintana Lowachinda} & (Thailand)\\
32. & Professor \textsc{M. D. Mavinkurve} & (India)\\
33. & Professor \textsc{R. S. Mishra} & (India)\\
34. & Professor \textsc{E. E. Moise} & (U.S.A.)\\
35. & Professor \textsc{P. H. Nagappa} & (India)\\
36. & Professor \textsc{N. S. Nagendranath} & (India)\\
37. & Professor \textsc{S. A. Naimpally} & (India)\\
38. & Mr. \textsc{Raghavan Narasimhan} & (India)\\
39. & Professor \textsc{V. V. Narlikar} & (India)\\
40. & Professor \textsc{M. H. A. Newman} & (U.K.)\\
41. & Professor \textsc{L. Nirenberg} & (U.S.A.)\\
42. & Professor \textsc{B. Y. Oke} & (India)\\
43. & Mr. \textsc{M. R. Pakpongsnit Snidwongs} & (Thailand)\\
44. & Professor \textsc{D. P. Patravalli} & (India)\\
45. & Professor \textsc{Hans Petersson} & (W. Germany)\\
46. & Dr. \textsc{Chr. Pommerenke} & (W. Germany)\\
47. & Professor \textsc{C. Racine} & (India)\\
48. & Mr. \textsc{S. Raghavan} & (India)\\
49. & Professor \textsc{K. G. Ramanathan} & (India)\\
50. & Dr. \textsc{S. S. Rangachari} & (India)\\
51. & Professor \textsc{H. E. Rauch} & (U.S.A.)\\
52. & Professor \textsc{A. L. Shaikh} & (Pakistan)\\
53. & Mr. \textsc{P. N. Shivakumar} & (India)\\
54. & Professor \textsc{U. N. Singh} & (India)\\
55. & Professor \textsc{M. H. Stone} & (U.S.A.)\\
56. & Professor \textsc{D. G. Sugathadasa} & (Ceylon)\\
57. & Professor \textsc{S. Tanbunyuen} & (Thailand)\\
58. & Mr. \textsc{S. K. Tekurkar} & (India)\\
59. & Principal \textsc{P. C. Vaidya} & (India)\\
60. & Mrs. \textsc{Vasanthi Venkatesh Rau} & (India)\\
61. & Mr. \textsc{M. K. Venkatesha Murthy} & (India)\\
62. & Professor \textsc{D. B. Wagh} & (India)\\
\end{longtable}

