
\chapter{Second South Asian Conference on Mathematical Education}

\begin{center}
\textbf{BOMBAY, 20-27 JANUARY 1960}

\bigskip

\textbf{\Large{PROGRAMME}}

\medskip

\textbf{Wednesday, January 20, 1960}
\end{center}


\begin{tabbing}
11.00 A.M. \hspace{2.5cm}\= \= Inauguration of the Conference\\
\> \> by Dr. H. J. Bhabha\\[0.2cm]
\> \> Presidential address\\
\> \> by Professor K. Chandrasekharan\\[0.2cm]
3.30 P.M. --- 4.10 P.M. \qquad \> \> Invited address\\
\> \> by Professor E. Artin on \textit{Contents and}\\
\> \> methods of an algebra course.
\end{tabbing}

\begin{center}
\textbf{Thursday, January 21, 1960}
\end{center}

\begin{tabbing}
~9.45 A.M. --- 11.00 A.M. \quad \= \= Working Group (Algebra)\\[0.2cm]
11.30 A.M. --- 12.10 A.M. \> \> Invited address\\
\> \> by Professor M. H. Stone on \textit{A beginning}\\
\>\>\textit{course in analytic geometry and calculus.}\\[0.2cm]
~3.30 P.M. --- 4.10 P.M. \> \> Invited address\\
\> \> by Professor T. A. A. Broadbent on\\
\> \> \textit{Place and teaching of co-ordinate}\\
\> \> \textit{geometry it the upper school.}\\[0.2cm]
~5.00 P.M. --- 5.40 P.M. \> \> Invited address\\
\> \> by Professor Y. Akizuki on \\
\> \> \textit{Introduction to determinants.}
\end{tabbing}

\begin{center}
\textbf{Friday, January 22, 1960}
\end{center}

\begin{tabbing}
~9.45 A.M. --- 11.00 A.M. \= \= Working Group (Geometry)\\[0.2cm]
11.30 A.M. --- 12.10 P.M. \> \> Invited address\\
\> \> by Professor W. Fenchel on \textit{A beginner's}\\
\> \> \textit{course in analytic geometry and}\\
\>\> \textit{linear algebra.}\\[0.2cm]
3.30 P.M. --- ~4.10 P.M. \> \> Invited address\\
\> \> by Professor Wolfgang Krull on \\
\> \> \textit{Analytical and projective geometry.}\\[0.2cm]
~5.00 P.M. --- ~5.40 P.M. \> \> Invited address\\
\> \> by Professor A. Lichnerowicz on \\
\> \> \textit{The role of the exterior calculus in geometry.}
\end{tabbing}

\begin{center}
\textbf{Saturday, January 23, 1960}
\end{center}

\begin{tabbing}
~9.45 A.M. --- 11.00 A.M. ~~\= \= Working Group (Algebra and
  Calculus)\\[0.2cm]
11.30 A.M. --- 12.10 P.M. \> \> Invited address\\
\> \> by Professor E. E. Moise on \textit{Geometry at}\\
\> \> \textit{the high school level.}
\end{tabbing}

\begin{center}
\textbf{Monday, January 25, 1960}
\end{center}

\begin{tabbing}
~9.45 A.M. --- 11.00 A.M. ~~\= \= Working Group (Analysis)\\[0.2cm]
11.30 A.M. --- 12.10 P.M. \> \> Invited address\\
by Professor M. H. A. Newman on \\
\textit{Topology in the first degree course.}\\[0.2cm]
3.30 P.M. --- 4.10 P.M. \> \> Invited address\\
\> \> by Professor A. D. Alexandrov on\\
\> \> \textit{Mathematics in the humanities.}
\end{tabbing}

\eject

\begin{center}
\textbf{Tuesday, January 26, 1960}
\end{center}


\begin{tabbing}
~9.45 A.M. --- 11.00 A.M. ~~~\= \= Working Group\\[0.2cm]
11.30 A.M. --- 12.00 \textsc{noon} \> \> Invited address\\
\> \> by Professor C. J. Eliezer on \textit{Progress of}\\
\> \> \textit{mathematical education in Malaya and}\\
\> \> \textit{Singapore.}\\[0.2cm]
12.10 P.M. --- 12.40 P.M. \> \> Invited address\\
\> \> by Ir. Soehakso on \textit{Progress of}\\
\> \>\textit{mathematical education in Indonesia.}\\[0.2cm]
~3.00 P.M. --- ~3.30 P.M. \> \> Invited address\\
\> \> by Professor S. Tanbunyuen on \\
\> \> \textit{Progress of mathematical education in}\\
\> \> \textit{Thailand.}
\end{tabbing}

\begin{center}
\textbf{Wednesday, January 27, 1960}
\end{center}

\begin{tabbing}
~9.45 P.M. --- 10.15 A.M. ~~~~ \= \= Invited address\\
\> \> by Professor A. L. Shaikh on  \textit{Progress}\\
\> \> \textit{of mathematical education in Pakistan.}\\[0.2cm]
10.25 A.M. --- 10.55 A.M. \> \> Invited address\\
\> \> by Principal D. G. Sugathadasa on \\
\> \> \textit{Progress of mathematical education in}\\
\> \> \textit{Ceylon.}\\[0.2cm]
12.00 \textsc{noon} --- 12.40 P.M. \> \>   Plenary session.
\end{tabbing}








