
\chapter{Second South Asian Conference on Mathematical Education}

\begin{center}
\textbf{BOMBAY, 20-27 JANUARY 1960}

\bigskip
\textbf{\Large{LIST OF PARTICIPANTS}}
\end{center}

\noindent
\textsc{Ceylon}

\smallskip
Principal D. G. \textsc{Sugathadasa}

Government Training College

Maharagama, Ceylon

\noindent
\textsc{Denmark}

\smallskip
Professor W. \textsc{Fenchel}

University of Copenhagen

\noindent
\textsc{France}

\smallskip
Professor H. \textsc{Cartan}

Institut Henri Poincar\'e

11, rue Pierre Curie

Paris 5

\medskip

Professor A. \textsc{Lichnerowicz}

Coll\`ege de France

Paris 5

\medskip
\noindent
\textsc{West Germany}

\smallskip
Professor \textsc{Emil Artin}

University of Hamburg

\smallskip

Professor \textsc{Wolfgang Krull}

University of Bonn

\medskip

Professor H. \textsc{Grauert}

University of G\"ottingen

\medskip

Dr. K. B. \textsc{Gundlach}

University of G\"ottingen

\medskip

Professor \textsc{Hans Petersson}

University of M\"unster

\medskip

Dr. \textsc{Chr. Pommerenke}

University of G\"ottingen

\medskip
\noindent
\textsc{India}

\smallskip
Dr. J. P. \textsc{Agarwal}

Agra University

\bigskip

Professor D. S. \textsc{Agashe}

University of Bombay

\bigskip

Professor T. J. \textsc{Balwani}

University of Bombay

\bigskip

Professor \textsc{Ram Behari}

University of Delhi

\bigskip

Dr. H. J. \textsc{Bhabha}

Tata Institute of Fundamental Research

\bigskip

Professor K. \textsc{Chandrasekharan}

Tata Institute of Fundamental Research

\bigskip
Dr. J. R. \textsc{Choksi}

Tata Institute of Fundamental Research

\bigskip

Mr. K. N. \textsc{Gowrisankaran}

Tata Institute of Fundamental Research

\bigskip

Professor K. R. \textsc{Gunjikar}

University of Bombay

\bigskip

Professor V. S. \textsc{Huzurbazar}

University of Poona

\bigskip

Professor V. S. \textsc{Krishnan}

University of Madras

\bigskip
 Professor M. D. \textsc{Mavinkurve}

University of Bombay

\bigskip

Professor R. S. \textsc{Mishra}

University of Gorakhpur

\bigskip

Professor P. H. \textsc{Nagappa}

University of Mysore

\bigskip

Professor N. S. \textsc{Nagendranath}

University of Patna

\bigskip
 
Professor S. A. \textsc{Naimpally}

University of Bombay

\bigskip

Mr. \textsc{Raghavan Narasimhan}

Tata Institute of Fundamental Research

\bigskip

Professor V. V. \textsc{Narlikar}

University of Banaras

\bigskip

Professor B. Y. \textsc{Oke}

University of Bombay

\bigskip

Professor D. P. \textsc{Patravali}

University of Bombay

\bigskip

Professor C. \textsc{Racine}

Loyola College

Madras 31

\bigskip

Mr. S. \textsc{Raghavan}

Tata Institute of Fundamental Research

\bigskip

Professor K. G. \textsc{Ramanathan}

Tata Institute Fundamental Research

\bigskip

Dr. S. S. \textsc{Rangachari}

Tata Institute of Fundamental Research

\bigskip

Mr. P. N. \textsc{Shivakumar}

Karnatak University

\bigskip

Professor U. N. \textsc{Singh}

University of Baroda

\bigskip

Mr. S. K. \textsc{Tekurkar}

Marathwada University

\bigskip

Principal P. C. Vaidya

Gujarat University

\bigskip

Mrs. \textsc{Vasanthi Venkatesh Rau}

Tata Institute of Fundamental Research

\bigskip

Mr. M. K. \textsc{Venkatesha Murthy}

Tata Institute of Fundamental Research

\bigskip

Professor D. B. \textsc{Wagh}

University of Bombay

\medskip
\noindent
\textsc{Japan}

\smallskip

Professor Y. \textsc{Akizuki}

Kyoto University

Kyoto

\bigskip

Professor R. \textsc{Kawai}

Kyoto University

Kyoto

\eject

 
Professor M. \textsc{Kuranishi}

Nagoya University

Nagoya

\medskip
\noindent
\textsc{Malaya}

\smallskip
Professor C. J. \textsc{Eliezer}

University of Malaya

Kuala Lumpur

\medskip
\noindent
\textsc{Pakistan}

\smallskip
Dr. L. M. \textsc{Chawala}
 
Government College

Lahore, W. Pakistan

\bigskip

Dr. \textsc{Syed Qasim Husain}

Rajshahi University 

East Pakistan

\bigskip

Professor A. L. \textsc{Shaikh}

Sind University

Hyderabad (Sind)

W. Pakistan

\medskip
\noindent
\textsc{Singapore}

\smallskip

Professor C. J. \textsc{Eliezer}

University of Malaya in Kuala Lumpur

\bigskip

Mr. R. M. \textsc{de Cruz}

Department of Education

University of Malaya in Singapore 

\medskip
\noindent
\textsc{Thailand}

\smallskip
Professor S. \textsc{Tanbunyuen}

Chulalongkorn University 

Bangkok

\bigskip

Miss \textsc{Chintana Lowachinda}

Chulalongkorn University

Bangkok

\medskip
\noindent
\textsc{United Kingdom}

\smallskip
Professor T. A. A. \textsc{Broadbent}

Royal Naval College, Greenwich

London S. E. 10

\bigskip

Professor M. H. A. \textsc{Newman}

University of Manchester

\medskip
\noindent
\textsc{U.S.A.}

\smallskip

Professor W. L. \textsc{Baily}

University of Chicago

\bigskip

Professor L. \textsc{Bers}

New York University

\bigskip

Professor E. E. \textsc{Moise}

University of Michigan

Ann Arbon, Michigan

\bigskip

Professor L. \textsc{Moise}

University of Michigan

Ann Arbor, Michigan

\bigskip

Professor L. \textsc{Nirenberg}

New York University

\bigskip

Professor H. E. \textsc{Rauch}

Yeshiva University 

New York 33, N. Y.

\bigskip

Professor M. H. \textsc{Stone}

Eckhart Hall

University of Chicago

Chicago 37, Illinois

\medskip
\noindent
\textsc{U.S.S.R.}

\smallskip

Professor A. D. \textsc{Alexandrov}

University of Leningrad

\bigskip

Professor B. V. \textsc{Gnedendko\footnote{Did not attend the conference}}

University of Kiev



