



\chapter{Introduction}

This\pageoriginale book originated from two courses given by the author at the Tata
Institute of Fundamental Reasearch during 1993. Lectures 1-14 are the
first course which was originally meant to be an exposition of the
recent topological rigidity result for non-positively curved manifolds
due to L.E. Jones and the author. Since the intent was to make the
proof of this result accessible to a wide audience, the author decided
to include material on surgery theory and controlled topology
prerequisite to understanding this proof. Th first 14 lectures are
consequently an introduction to rather than an exposition of the
published work on topological rigidity. The last 6 lectures are the
second course which concerns the question of smooth rigidity for
non-positively curved manifolds. Lecture 15 gives a motivating example
of an exotic expanding endomorphism constructed many years earlier by
L.E. Jones and the author. Then lectures 16-19 contains an exposition
of some of the counterexamples to smooth rigidity found by L.E. Jones
and the author. Not all of the technical details are given. But it is
hoped that the references made to the literature will allow the
curious reader to satisfy himself about them. The final lecture is a
brief discussion (with references) to some more recent results on
topological and smooth rigidity.

The author wishes to thank the faculty of the Tata Institute for their
kind invitation to give these courses and for publishing the resulting
lectures. He also thanks Shashidhar Upadhyay for his generous help
both during the course and in preparing the lectures for
publication. Finally, he wishes to thank Marge Pratt for the splendid
typing of these lectures.\footnote{The author was supported in part by the National Science Foundation.}
