\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf On the Mean-Value and}\\[5pt]
{\Large\bf Omega-Theorems for the}\\[5pt]
{\Large\bf Riemann Zeta-Function}
\vfill

{\large\bf K. Ramachandra}
\vfill

{\bf Tata Institute of Fundamental Research}

{\bf Bombay}

{\bf 1995}
\end{center}

\eject

\thispagestyle{empty}

\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf On the Mean-Value and}\\[5pt]
{\Large\bf Omega-Theorems for the}\\[5pt]
{\Large\bf Riemann Zeta-Function}
\vfill

{\large\bf K. Ramachandra}
\vfill

Published for the\\

{\bf Tata Institute of Fundamental Research}
\vfill

{\Large Springer-Verlag}\\[5pt]
Berlin Heidelberg New York Tokyo\\[5pt]
1995
\end{center}
\eject

\thispagestyle{empty}

\noindent
{\large\bf K. Ramachandra}\\[5pt]
School of Mathematics\\
Tata Institute of Fundamental Research\\
Bombay 400 005, India
\vfill

\noindent
{\bf Copyright \copyright 1995 Tata Institute of Fundamental Research,\hfil\break
  Bombay} 
\vfill

\noindent
ISBN 3-540-58437-4 Springer-Verlag Berlin Heidelberg\hfil\break New York Tokyo

\noindent
ISBN 0-387-58437-4 Springer-Verlag New York Berlin\hfil\break Heidelberg Tokyo
\vfill


\noindent
No part of this book may be reproduced in any form
by print, microfilm or any other means without written
permission from the Tata Institute of Fundamental Research,
Colaba, Bombay 400 005, India
\vfill


\noindent
This book has been produced from the Camera
Ready text provided by the 
Tata Institute of Fundamental Research, Bombay  


\noindent
Printed and Published by Claus Michaletz,
Springer-Verlag, Heidelberg, Germany. Printed in India.  

\eject

\thispagestyle{empty}
~
\vfill

\begin{center}

\noindent\rule{\textwidth}{1pt}

\textit{To Professors}\\[5pt]
{\large\bf Alan Baker,} FRS\\
and\\
{\large\bf Hugh L. Montgomery}

\noindent\rule{\textwidth}{1pt}
\vfill

\end{center}


\chapter{Preface}

This monograph is meant to be an appendix to the Chapters VII and VIII of the famous book of E.C. TITCHMARSH (second edition) revised and edited by D.R. HEATH-BROWN. Recently there are a few books on these topics but I am sure that the material presented in this book is new and that this book is not a repetition. There are a few important theorems which are new, especially the asymptotic formula as $H \to \infty$ for
$$
\min\limits_{I,|I| = H} \max\limits_{t \in I} |(\zeta (1+ it))^z|, z = e^{i\theta},
$$
where $\theta$ is a real constant and the minimum is taken as $I$ runs over all $t$-intervals (of fixed length $H$) contained in $[2, \infty)$. I hope that the style of writing motivates the topic and is also readable. Many of the topics deal with  the joint work of mine with Professor R. BALASUBRAMANIAN to whom my indebtedness is due. I owe a lot to the famous book of E.C. TITCHMARCH mentioned already, to the twelve lectures on RAMANUJAN by G.H. HARDY, Distribution of prime numbers by A.E. INGHAM, Riemann zeta-function by K. CHANDRASEKHARAN, and Topics in Multiplicative Number Theory by H.L. MONTGOMERY. Recently I am also indebted to the book Arithmetical functions by K. CHANDRASEKHARAN, Sieve methods by H.-E.\break RICHERT, A method in the theory of exponential sums by M. JUTILA, and to the two books Riemann zeta-function and Mean values of the Riemann zeta-function by A. IVI\'C. I owe a lot (by way  of their encouragement at all stages of my work) to Professors P.X. GALLAGHER, Y. MOTOHASHI, E. BOMBIERI, H.L. MONTGOMERY, D.R. HEATH-BROWN, H.-E. RICHERT, M. JUTILA, K. CHANDRASEKHARAN, A. BAKER, FRS, A. IVI\'C and M.N. HUXLEY. Particular mention has to be made of Professor M. JUTILA for his many encouraging letters and his help in various ways.    

I have to give an excuse for referring to too many papers of myself
and that of R. BALASUBRAMANIAN. The excuse is that I deal with an
appendix to Chapters VII and VIII of the famous book of
E.C. TITCHMARSH as mentioned already and that I can do better justice
(by way of a good exposition when writing about our work). 

I acknowledge some important help given to me by
Dr. A. SANKA\-RANARAYANAN and Sri K. SOUNDARARAJAN. 

Next I am indebted to Professor S. RAMANAN  for agreeing to publish this material in the Lecture Notes series of TIFR.

Lastly I offer my sincere thanks to Sri D.B. SAWANT for his excellent typing of the manuscript in TEX.

\bigskip

\bigskip


\hfill{\large\bf K. RAMACHANDRA}



