\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Siegel Modular Forms and}\\[5pt] 
{\Large\bf Representation by Quadratic Forms}
\vskip 1cm

{\bf By}\\
\medskip

{\large\bf Y. Kitaoka}
\vfill

{\bf Tata Institute of Fundamental Research}


{\bf Bombay}\\


{\bf 1986}
\end{center}
\eject

\thispagestyle{empty}

\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Siegel Modular Forms and}\\[5pt] 
{\Large\bf Representation by Quadratic Forms}
\vskip 1cm

{\bf By}
\medskip

{\large\bf Y. Kitaoka}
\vfill

Published for the 
\medskip




{\bf Tata Institute of Fundamental Research}

{\bf Springer--Verlag}


{\bf Berlin Heidelberg New York Tokyo}

{\bf 1986}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
{\bf Author}

{\large\bf Y. Kitaoka}\\
Department of Mathematics\\
Faculty of Science\\
Nagoya University\\
Chikusa--Ku, Nagoya, 464\\
JAPAN
\vfill

\copyright \; Tata Institute of Fundamental Research, 1986\\
\vfill

\noindent\rule\textwidth{1pt}

ISBN 3-540-16472-3 Springer--Verlag, Berlin. Heidelberg.\\ 
New York. Tokyo

ISBN 0-387-16472-3 Springer--Verlag, New York.\\ 
Heidelberg. Berlin. Tokyo

\noindent\rule\textwidth{1pt}
\vfill

\parbox{0.7\textwidth}{%
No part of this book may be reproduced in any form
by print microfilm or any other means without written
permission from the Tata Institute of Fundamental
Research, Colaba, Bombay 400 005}
\vfill

Printed by K. M. Aarif at Paper Print India, Worli,

Bombay 400 018 and published by H. Goetze,

Springer--Verlag, Heidelberg, West Germany,
\vfill

Printed In India
\end{center}
\eject

\chapter{Preface}

These are based on my lectures at the Tata Institute of Fundamental
Research in 1983-84. They are concerned with the problem of
representation of positive definite quadratic forms by other such
forms. 

\S~1.6 and Chapter~2 are added, besides lectures at the Institute, by
Professor Raghavan (who also wrote up \S\S~1.1--1.4) and myself
respectively.

I would like to thank Professor Raghavan and the Tata Institute for
their hospitality.
\vskip 1cm

\hfill {\large\bf Y. Kitaoka}\qquad\, 
