
\thispagestyle{empty}

\noindent
{\bf\huge Contents}

\vskip 1cm

\thispagestyle{empty}

\noindent
\renewcommand{\arraystretch}{1.7}
\begin{longtable}[l]{r>{\raggedright}p{9cm}r}
1. & \textsc{S. S. Abhyankar~:} Resolution of Singularities of Algebraic Surfaces & ?? \\
2. & \textsc{M. Artin~:} The Implicit Function Theorem in Algebraic Geometry & ?? \\
3. & \textsc{B. J. Birch~:} Diophantine Analysis and Modular Functions & ?? \\
4. & \textsc{A. Borel~:} On the Automorphisms of Certain Subgroups of Semi-Simple Lie Groups & ?? \\
5. & \textsc{A. Borel} and \textsc{J. Tits~:} On ``Abstract'' Homomorphisms of Simple Algebraic Groups  & ?? \\
6. & \textsc{J. W. S. Cassels~:} Rational Points on Curves of Higher Genus & ?? \\
7. & \textsc{B. Dwork~:} A Deformation Theory for Singular Hyper-surfaces & ?? \\
8. & \textsc{P. A. Griffiths~:} Some Results on Algebraic Cycles on Algebraic Manifolds & ?? \\
9. & \textsc{A. Grothendieck~:} Standard Conjectures on Algebraic Cycles & ?? \\
10. & \textsc{H. Hironaka~:} Formal Line Bundles along Exceptional Loci & ?? \\
11. & \textsc{F. Hirzebruch} and \textsc{K. J\"anich~:} Involutions and Singularities  & ?? \\
12. & \textsc{J-I. Igusa~:} Geometric and Analytic Methods in the Theory of Theta-Functions & ?? \\
13. & \textsc{Yu. I. Manin~:} On Some Groups Related to Cubic Hyper-surfaces & ?? \\
14. & \textsc{T. Matsusaka~:} On Canonically Polarized Varieties & ?? \\
15. & \textsc{D. Mumford~:} Bi-Extensions of Formal Groups & ?? \\
16. & \textsc{M. Nagata~:} Some Questions on Rational Actions of Groups & ?? \\
17. & \textsc{M. S. Narasimhan} and \textsc{S. Ramanan~:} Vector Bundles on Curves & ?? \\
18. & \textsc{C. S. Seshadri~:} Mumford's Conjecture for $GL(2)$ and Applications & ?? \\
19. & \textsc{T. A. Springer~:} The Unipotent Variety of a Semi-Simple Group  & ?? \\
20. & \textsc{J.-L. Verdier~:} Base Change for Twisted Inverse Image of Coherent Sheaves & ?? \\
21. & \textsc{A. Weil~:} Zeta-Functions and Mellin Transforms & ?? \\
\end{longtable}

\thispagestyle{empty}
