\phantom{a}
\thispagestyle{empty}
\begin{center}
{\Large\bf Lectures on}\\[5pt]
{\Large\bf Topics in Stochastic Differential Equations}
\vskip 1cm

{\bf By}

{\large\bf Daniel W. Stroock}
\vfill

{\bf Tata Institute of Fundamental Research}

{\bf Bombay}

{\bf 1982}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
{\large\bf Lectures on}\\[5pt]
{\large\bf Topics in Stochastic Differential Equations}
\vskip 1cm

{\bf By}

{\large\bf Daniel W. Stroock}
\vfill

{Lectures delivered at the}\\[5pt]
{\bf Indian Institute of Science, Bangalore}\\[5pt]
{under the}\\[5pt]
{\bf T.I.F.R.--I.I.SC. Programme in applications of}\\[5pt]
{\bf Mathematics}
\vfill

{\bf Notes by}\\[5pt]
{\large\bf Satyajit Karmakar}

\vfill
{Published for the}\\[5pt]
{\bf Tata Institute of Fundamental Research, Bombay}\\[5pt]
{\bf Springer-Verlag}\\[5pt]
{Berlin Heidelberg New York}\\[5pt]
{\bf 1982}
\end{center}
\eject

\thispagestyle{empty}
\begin{center}
{\bf Author}\\[5pt]
{\large\bf Daniel W. Stroock}\\[5pt]
{Department of Mathematics}\\[3pt]
{University of Colorado}\\[3pt]
{Boulder, Colorado 80309}\\[3pt]
{\bf U.S.A.}

\vfill

{\large\bf \copyright Tata Institute of Fundamental Research, 1981}


\rule{\textwidth}{.5pt}

ISBN 3-540-11549-8 Springer-Verlag, Berlin. Heidelberg. New York

ISBN 0-387-11549-8 Springer-Verlag, New York. Heidelberg. Berlin

\rule{\textwidth}{.5pt}

\vfill

\parbox{0.7\textwidth}{
No part of this book may be reproduced in any form by print, microfilm
or any other means without written permission from the Tata Institute
of Fundamental Research, Colaba, Bombay 400 005
}
\vfill

Printed by N. S. Ray at the Book Centre Limited,

Sion East, Bombay 400 022 and published by H. Goetze,

Springer-Verlag, Heidelberg, West Germany

\bigskip

{\large\bf Printed in India}
\end{center}

\eject

\thispagestyle{empty}

\chapter*{Preface}

THESE NOTES are based on five weeks of lectures given during December
1980 and January 1981 at T.I.F.R. in Bangalore. My purpose in these
lectures was to provide some insight into the properties of solutions
to stochastic differential equations. In order to read these notes,
one need only know the basic It\^o theoryof stochastic integrals. For
example, H.P. McKean's {\em Stochastic Integrals} (Academic Press,
1969) contains all the background material.

After developing a little technical machinery, I have devoted Chapter
I to the study of solutions of S.D.E.'s as a function of the initial
point. This topic has been discussed by several authors; the treatment
given here is based on a recent paper by H. Kunita (to appear in the
Proceedings of the 1980 L.M.S. conference at Durham). In fact, the
only way in which the present treatment differs from this is that I
have been a little more careful about the integrability estimates.

Chapter II is devoted to the study of solutions as a function of
time. A large part of this material is adapted from my work with
S.R.S. Varadhan (``On the support of diffusion processes with
applications to the strong maximum principle'', Proc. 6th Berkeley
Symp. on Math. Stat. and Prob., Vol.III (1970)). The presentation of
this material has been greatly aided by the incorporation of ideas
introduced by Y. Takahashi and S. Watanabe in their paper ``The
probability functionals of diffusion processes'' (to appear in the
Proceedings of the 1980 L.M.S. conference at Durham). To intorduce the
reader to their work, in the last section of Chapter II, I have
derived a very special case of the general result derived in the paper
by Takahashi and Watanabe.

I would like to thank S. Karmakar for his efforts in guiding these
notes to completion. Also, I am grateful to R. Karandikar for his
useful comments on these notes. Finally, it gives me pleasure to
express my gratitude to K.G. Ramanathan and the Tata Institute for the
opportunity to visit India.




