\chapter{Lecture 32}\label{chap32:lec32}

\textit{Let\pageoriginale $\mathscr{S'}$ and $\mathscr{S}$ be sheaves of
  $\mathfrak{a}$- modules and let $\mathscr{S'}$ have property
$(a)$. If $f$ and $g$ are two homomorphisms of  $\mathscr{S'}
\rightarrow \mathscr{S}$, the set of points $x$ for which $f
| S'_x = g| S'_x$ is an open set}. 

\begin{proof}
Let $W$ be the set of points $x$ for which $f | S'_x = g| S'_x$ and
let $x_o \in W$. Since $\mathscr{S'}$ has property $(a)$, there is an
epimorphism 
$$
\phi : \sum^k_{i=1} \mathfrak{a}_U \rightarrow \mathscr{S'}_U 
$$
for some neighbourhood $U$ of $x_o$. Then since $x_o \in W$, $f \phi h^j
l_{x_o} = g \phi h^j l_{x_o}$ $(j = 1, \ldots , k)$, and hence for some
open set $V_j$, with $x_0 \in V_j \subset U$, 
$$
f \phi h^j 1 = g \phi h^j 1 : V_j \rightarrow S. 
$$
\[
\xymatrix{
V\ar[r]^1 & \mathfrak{a}_V \ar[r]^{h^j} & \sum^k_{i=1} \mathfrak{a}_V
\ar[r]^{\phi} & \mathscr{S}'_V \ar@/_1pc/[r]_g \ar@/^1pc/[r]^f&
\mathscr{S}_V 
}
\]
\end{proof}

Let $V = \bigcap^k_{j=1} V_j$. If $\sum^k_{i-1} a_i \in \sum^k_{i-1}
A_i$ with $x \in V$,  
then
\begin{align*}
f \phi (\sum^k_{i=1} a_i) & = f \phi (\sum^k_{i=1} h^i a_i) =
\sum^k_{i=1} a_i f \phi h^i 1_x \\ 
& = \sum^k_{i=1} a_i g \phi h^i 1_x = g \phi (\sum^k_{i=1} a_i). 
\end{align*}

Hence $f \phi |\sum^k_{i=1} \mathfrak{a}_V = g \phi | \sum^k_{i=1}
\mathfrak{a}_V$ and, 
since $\phi$ is an epimorphism, $f |\mathscr{S'}_V = g |
\mathscr{S'}_V$. Thus $x_o \in V \subset W$ with $V$ open. Hence $W$
is an open set. 

The\pageoriginale following result deals with the extension of stalk homomorphisms. 

\textit{Let $\mathscr{S'}, \mathscr{S}$ be sheaves of $\mathfrak{a}$-
modules such that $\mathscr{S'}$ is coherent and
$\mathscr{S}$ has property $(a)$. At a point $x \in
X$, let $f  : S'_x \rightarrow S_x$ be a homomorphism of $A_x$
modules. Then there is a neighbourhood $U$ of $x$ and
  a homomorphism  $f : \mathscr{S'}_U \rightarrow \mathscr{S}_U$
whose restriction to  $S'_x$ is $f_x$.} 

\begin{proof}
Since $\mathscr{S'}$ and $\mathscr{S}$ have property $(a)$, there is a
neighbourhood $W$ of $x$ and epimorphisms 
\begin{align*}
\phi & : \sum^p_{j=1} \mathfrak{a}_W \rightarrow \mathscr{S'}_W , \\
\text{and } \qquad  
\theta & : \sum^q_{j=1} \mathfrak{a}_W \rightarrow \mathscr{S}_W.
\end{align*}

For each $j = 1, \ldots , p$, choose an element $\sum^q_{i=1} a^j_i
\in \sum^q_{i=1} A_x$ such that  
$$
\theta \left(\sum^q_{i=1} a^j_i \right) = f_x \phi h^j l_x'
$$
and choose sections
$$
\eta_j : V_j \rightarrow \sum^q_{i=1} \mathfrak{a}_{V_j} 
$$
with $x \in V_j \subset W, V_j$ open, such that $\eta_j(x) =
\sum^q_{i=1} a^j_i$, $j=1, \ldots , p$. Let the homomorphism 
$$
g_j : \mathfrak{a}_{v_j} \rightarrow \sum^q_{i=1} \mathfrak{a}_{v_j} 
$$
be defined by $g_j(a) = a \cdot \eta_j (\pi (a))$. Then, for $a \in A_x$,
\begin{align*}
\theta g_j (a) & = \theta (a \cdot \eta_j (x)) = a \cdot \theta(\sum^q_{i=1}
a^j_i)\\ 
& = a \cdot f_x \phi h^j 1_x = f_x \phi h^j (a). 
\end{align*}\pageoriginale

Then the homomorphisms $\{g_j \} j = 1, \ldots , p$, induce a
homomorphism  
$$
g : \sum^p_{i=1} \mathfrak{a}_v \rightarrow \sum^q_{i=1} \mathfrak{a}_v
$$ 
where $V = \cap^p_{j=1} V_j $, such that $\theta_g| \sum^p_{i=1}
A_x = f_x \phi$. 
\[
\xymatrix{
\sum^r_{k=1} \mathfrak{a}_U \ar[r]^{\psi} & \sum^p_{j=1}
\mathfrak{a}_U \ar[r]^{\phi} \ar[d]_g & \mathscr{S}'_U
\ar[r]\ar@{-->}[d]^{f}_{f_x} & 0\\
& \sum^q_{i=1} \mathfrak{a}_U \ar[r]^{\theta} & \mathscr{S}_U & 
}
\]

Since $\mathscr{S'}$ has property $(b)$, there is an open set $Y$ with
$x \in Y \subset V$, and homomorphism 
$$
\psi : \sum^r_{k=1} \mathfrak{a}_Y \rightarrow \sum^p_{j=1}
\mathfrak{a}_Y 
$$
such that $\im \psi = ker \phi$. Then 
$$
\theta_g \psi \left| \sum^r_{k=1} A_x = f_x \phi \psi \right|
\sum^r_{k=1} A_x = 0 
$$
by exactness. Hence by the previous result, there is an open set $U$
with $x \in U \subset Y$, such that the homomorphism $\theta_g \psi \Big|
\sum^r_{k=1} \mathfrak{a}_U$ coincides with the zero homomorphism. Therefore
$\theta_g$ induces a homomorphism 
$$
f: \left(\sum^p_{j=1} \mathfrak{a}_U \right) / \im \psi \rightarrow 
\mathscr{S}_U. 
$$

We\pageoriginale can identify this quotient $(\sum^p_{j=1}
\mathfrak{a}_U) / \im \psi $ with 
$\mathscr{S'}_U$ so that $\phi$ becomes the natural homomorphism; then
$f$ is a homomorphism $f: \mathscr{S'}_U \rightarrow \mathscr{S}_U$
with $f \phi = \theta_g \Big| \sum^p_{j=1} \mathfrak{a}_u$. If $s \in
S'_x$ since $\phi$ is an epimorphism there is some element
$\sum^p_{j=1} a_j \in \sum^p_{j=1} A_x$ such that $s = \phi
(\sum^p_{j=1} a_j)$. Then  
\begin{align*}
f(s) & = f \phi (\sum^p_{j=1} a_j) = \theta_g (\sum^p_{j=1} a_j) \\ 
& = f_x \phi (\sum^p_{j=1} a_j) = f_x (s);
\end{align*}
i.e., the restriction of $f$ to $S'_x$ is $f_x$, $q.e.d$. 
\end{proof}

\textit{Let $Y \subset X$ and either, let $x$ be paracompact and normal
  and $Y$ closed, or, let $X$ be hereditarily paracompact and
  normal. Let $\mathscr{S'}$, $\mathscr{S}$ be sheaves of $\mathfrak{a}$-
  modules over $X$ such that $\mathscr{S'}$ is coherent and
  $\mathscr{S}$ has property $(a)$. If $f : \mathscr{S'}_y \rightarrow
  \mathscr{S}_y$ is a homomorphism of sheaves of $\mathfrak{a}_y$
  modules, there exists an open set $U$ with $Y \subset U$, and a
  homomorphism $g : \mathscr{S'_U} \rightarrow \mathscr{S}_U$ such
  that $g | S'_y = f$.} 

\begin{proof}
By the previous result, for each point $y \in Y$ there is an open set
$V_y$ in $X$ with $x \in V_y$ and a homomorphism $\phi_y :
\mathscr{S'}_{v_y} \rightarrow \mathscr{S}_{V_y}$ such that $\phi_y \Big| S'_y
= f \Big| S'_y$. Then by the first result of this lecture, the set of 
points of $V_y \cap Y$ at which $\phi_y = f$ is open in $Y$. Hence there is
a set $W_y$ open in $X$ with $y \in W_y \subset V_y$ such that $\phi_y
\Big|\mathscr{S'}_{W_y \cap Y} = f \Big| \mathscr{S'}_{W_y \cap Y}$. 
\end{proof}

We\pageoriginale now show that there are systems $\{ G_i \}_{i \in I}$ and $\{
H_i\}_{i \in I}$ of open sets of $X$ such that, if $G
=\bigcup\limits_{i \in I} G_i$,  
\begin{enumerate}[(i)]
\item $\bar{H}_i \cap G \subset G_i$,

\item the system $\{ G_i \}$ is locally finite in $G$,

\item $Y \subset \bigcup \limits_{i \in I} H_i$,

\item each $G_i$ is contained in some $W_y$.
\end{enumerate}

\begin{enumerate}[(1)]
\item If $X$ is paracompact and normal and $Y$ is a closed subset of
  $X$, then the covering $\{ X - Y, W_y \}_{y \in Y}$ of $X$ has a
  locally finite refinement $\{ G_j \}_{j \in j}$, and the covering
  $\{ G_j \}_{j \in J}$ can be shrunk to a covering $\{ H_j \}_{j
    \in J}$ with $\bar{H}_j \subset G_j$. Let $I \subset J$ be the
  set of indices for which $G_j \cap Y$ is not empty. Then, for $i \in
  I$, $G_i$ is not contained in $X-Y$ and hence is contained in some
  $W_y$. Clearly $Y \subset \bigcup\limits_{i \in I} H_i$ and
  conditions (i), (ii), (iii), (iv) are satisfied. 

\item If $X$ is hereditarily paracompact and normal, then $G = \bigcup
  \limits_{y \in Y} W_y$ is paracompact and normal. Then there is a
  locally finite refinement $\{ G_i \}_{i \in I}$ of the covering $\{ W_y
  \}_{y \in Y}$ of $G$. Since $G$ is normal, the covering $\{ G_i
  \}_{i \in I}$ of $G$ can be shrunk to a covering $\{H_i \}_{i \in
    I}$ with $\bar{H}_i \cap G \subset G_i$. The sets $G_i$, $H_i$
  being open in $G$ are  open in $X$. Conditions (i), (ii), (iii),
  (iv) are thus satisfied. 
\end{enumerate}

Since $G_i$ is contained in some $W_y$, there are homomorphisms $\psi_i
: \mathscr{S'}_{G_i} \rightarrow \mathscr{S}_{G_i}$ such that $\psi_i
\Big| \mathscr{S'}_{G_i \cap Y} = f  \Big| \mathscr{S'}_{G_i \cap
  Y}$. Let $E_{ij}$\pageoriginale be the set of points $x \in
\bar{H}_i \cap \bar{H}_j \cap G$ at which 
$\psi_i |S'_x \neq \psi_j | S'_x$; then $E_{ij}$ is closed in $G$. Let
$E = \bigcup \limits_{i,j} E_{ij}$; it is the union of a locally
finite system of closed sets in $G$, hence is closed in $G$. Let $U =
G - E$, then $U$ is open in $G$, hence open in $X$, and $Y \subset
U$. 

Let $g : \mathscr{S'}_U \rightarrow \mathscr{S}_U$ be defined as
follows: For $x \in \bar{H}_i \cap U$ let $g | S'_x = \psi_i
|S'_x$. This gives a consistent definition of $g$, and $g$ is
continuous on each closed set $S'_{\bar{H}_i \cap U}$ of a locally
finite system in $S'_U$ (These closed sets cover $S'_U$). Thus $g$ is a
sheaf homomorphism and $g | \mathscr{S'}_Y =f $. 

The above result for the case when $X$ paracompact and normal is more
useful in applications. In particular, the above results are when both
$\mathscr{S'}$ and $\mathscr{S}$ are coherent sheaves of
$\mathfrak{a}-$modules.   

\begin{exam}%exe 35
Let $T$ be the space of ordinal numbers $\le \omega_1$ with the
topology induced by the order, let $Q$ be the space of ordinal numbers
$\le \omega_o$ and let $X = T \times Q$. Then $X$ is compact Hausdorff
and hence paracompact normal. Let $Y_1 = (T-(\omega_1)) \times \omega_o$,
$Y_2 = \omega_1 \times (Q - (\omega_o))$ and $Y = Y_1 \cup Y_2$. Let
$\mathfrak{a} = \mathscr{S'} = \mathscr{S} = Z_2$, then $\mathscr{S}$ is
coherent. Let $f : \mathscr{S}_Y \rightarrow \mathscr{S}_Y$ be the
homomorphism which is the identity on $Y_1$ and is zero on $Y_2$,
There is no extension of $f$ over an open set containing $Y$. 
\end{exam}

\textit{Let $Y \subset X$, and let $\mathscr{S}$ be a coherent sheaf 
  of $\mathfrak{a}$ modules over $X$. Then the restriction
  $\mathscr{S}_Y$ is a coherent sheaf of $\mathfrak{a}_y$ modules}.  

\begin{proof}
Since\pageoriginale $\mathscr{S}$ has property $(a)$, for each $y \in
Y$ there is an 
open set $W$ of $X$ with $y \in W$ and an epimorphism $\theta :
\sum^{p}_{i=1} \mathfrak{a}_W\rightarrow \mathscr{S}_W$. Then the restriction
$\theta \Big| \sum^{p}_{i=1} \mathfrak{a}_{W \cap Y} :  \sum^{p}_{i=1}
\mathfrak{a}_{W \cap Y} \rightarrow \mathscr{S}_{W \cap Y}$ is an
epimorphism. Thus $\mathscr{S}_Y$ has property  $(a)$.  
\end{proof}

To prove that $ \mathscr{S}_Y$ has property $(b)$, let $\theta ;
\sum^k_{i=1} \mathfrak{a}_{W \cap Y} \rightarrow \mathscr{S}_{W \cap Y}$ be a
homomorphism where $W$ is an open set in $X$, and let $y \in W \cap
Y$. Choose a section $f_i : V_i \rightarrow S, (i = 1, \ldots , k) y
\in V_i$, through $\phi h^i 1_y \in S_y$ and let $V = \bigcap^k_{i=1}
V_i$. There is a homomorphism $\phi' : \sum^k_{i=1} \mathfrak{a}_V
\rightarrow \mathscr{S}_V$ defined by 

\noindent
$\phi' \sum^k_{i=1} a_i = \sum^k_{i=1} a_i f_i \pi (a_i)$. If
$\sum^k_{i=1} a_i \in \sum^k_{i=1} A_y$, then  

\noindent
$\phi' \sum^k_{i=1} a_i = \sum^k_{i=1} a_i f_i (y) =
\sum^k_{i=1} a_i \phi h^i 1_y \phi \sum^k_{i=1} h^i a_i = \phi
\sum^k_{i=1} a_i$.  

 Since the set of points of $Y$ where $\phi' = \phi$ is open in $Y$, there
is an open set $G$ of $X$ with $y \in G \subset V \cap W$, such that
$\phi' \Big| \sum^k_{i=1} \mathfrak{a}_{G \cap Y} = \phi \Big|
\sum^k_{i=1} \mathfrak{a}_{G \cap  Y}$. Since $\mathscr{S}$ has
property $(b)$, there is an open set 
$U$ with $y \in U \subset G$, and a homomorphism 
$$
\psi' : \sum^1_{i=1} \mathfrak{a}_U \rightarrow \sum^k_{i=1}
\mathfrak{a}_U 
$$
such that the sequence 
$$
\sum^1_{i=1} \mathfrak{a}_U \xrightarrow{\psi'} \sum^k_{i=1} \mathfrak{a}_U
\xrightarrow{\phi'} \mathscr{S}_U 
$$
is exact. Then if $\psi = \psi' \Big| \sum^1_{i=1} \mathfrak{a}_{U
  \cap Y}$, the sequence 
$$
\sum^1_{i=1} \mathfrak{a}_{U \cap Y} \xrightarrow{\psi}
\sum^k_{i=1} \mathfrak{a}_{U \cap Y} \xrightarrow{\phi}
\mathscr{S}_{U\cap Y} 
$$
is exact. Thus $\mathscr{S}_Y$ has property $(b)$.

