\thispagestyle{empty}
\begin{center}
{\Large\bfseries Lectures on}\\[5pt]
{\Large\bfseries Nonlinear Waves And Shocks}
\vfill

{\bf By}
\medskip

{\large\bf Cathleen S. Morawetz}
\vfill
 
{\bf Tata Institute  Of Fundamental Research}

{\bf Bombay}

{\bf 1981}
\end{center}

\eject

\thispagestyle{empty}

\begin{center}
{\Large\bfseries Lectures on}\\[5pt]

{\Large\bfseries Nonlinear Waves And Shocks}
\vfill

{\bf By}
\medskip

{\large\bf Cathleen S. Morawetz}
\vfill


Lectures delivered at the 
\medskip

{\bf Indian Institute of Science, Bangalore}
\medskip

under the 
\medskip

{\bf T.I.F.R. --- I.I.SC. Programme In Applications of}
\medskip

{\bf Mathematics}
\vfill

{\bf Notes by}
\medskip

{\large\bf P.S. Datti}
\vfill

Published for the 
\medskip

{\bf Tata Institute  of Fundamental Research, Bombay}
\vfill

Springer--Verlag
\medskip

Berline-Heidelberg--New York
\medskip

{\bf 1981}
\end{center}

\eject

\thispagestyle{empty}
\begin{center}
{\bf Author}
\medskip

{\large\bf Cathleen S. Morawetz}
\bigskip

Courant Institute of Mathematical Sciences\\
New York University\\
251, Mercer Street\\
New York N.Y. 10012\\
U.S.A.
\vfill

{\bf\copyright \quad Tata Institute of Fundamental Research, 1981}
\vfill

\noindent\rule{\textwidth}{1pt}

ISBN 3--540--10830--0 Springer--Verlag, Berlin Heidelberg New York

\medskip

ISBN 0--387--10830--0 Springer--Verlag, New York Heidelberg Berline

\noindent\rule{\textwidth}{1pt}
\medskip

\parbox{0.7\textwidth}{No part of this book may be reproduced in any
  form  by point, microfilm or any other means without 
written permission from the Tata Institute of 
Fundamental Research, Colaba, Bombay 400 005}
\vfill

Printed by N. S. Ray at The Book Centre Limited, \\
Sion East, Bombay 400 022 and published by H. Goetz,\\
Springer-Verlag, Heidelberg, West Germany\\
\vfill

Printed In India
\end{center}



\chapter{Preface}


THESE LECTURE NOTES are the outcome of a six week course with the
Bangalore applied mathematics group of the Tata Institute. It is a
pleasure to recall the enthusiasm and energy of the participants. The
lectures were on introduction to certain aspects of gas dynamics
concentrating on some of the currently most important nonlinear
problems, important not only from the engineering or computational
point of view but also because they offer great mathematical
challenges. The notes, I hope, touch on both these aspects. 


I am indebted to Professor K.G. Ramanathan for inviting me in the
first place and for making my visit so enjoyable and stimulating. To
P.S. Datti, who cooperated in writing these notes and worked and
reworked them, go my very deep thanks. I would also like to thank
P.P. Gopalakrishnan who reproduced them so well. 
\bigskip


\begin{flushright}
{\large\bf Cathleen S. Morawetz}
\medskip


New York

December 1980
\end{flushright}

