\setcounter{pageoriginal}{552}
\begin{thebibliography}{ABCDEFGHI}
\bibitem=2pt
\bibitem[Bass(1973)]{Bass}\pageoriginale
{H. Bass} Some problems in``classical'' algebraic $K$-theory \textit{Lecture Notes in Math.} No. 342, Springer-Verlag, New-York (1973).

\bibitem[Bloch(1976)]{Blocha}
S. Bloch} Lectures on algebraic cycles, \textit{Duke Univ. Math. Ser.} IV, Duke Univ. Press, Durham (1976).

\bibitem[Bloch(1975)]{Blochb}
{S. Bloch} $K_2$ of artinian $\mathbb{Q}$-algebras with applications to algebraic cycles, \textit{Comm. Alg}., 3(1975) 405--426.

\bibitem[Collino(1981)]{Collino}
{A. Collino} Quillen's $\mathscr{K}$-theory and algebraic cycles on almost non-singular varieties, \textit{Ill. J. Math}., 25(1981) 654--666.

\bibitem[Coombes(1982)]{Coombes}
{K. R. Coombes} V. Srinivas. Relative $K$-theory and vector bundles on certain singular varieties, \textit{Invert. Math}., 70(1982) 1--12.

\bibitem[Hartshorne(1977)]{Hartshorne}
{R. Hartshorne} Algebraic Geometry, \textit{Grad. Texts in Math.} No. 52, Springer-Verlag, New York(1977).

\bibitem[Van der Kallen(1971)]{Vander}
{W. Van der Kallen} Le $K_2$ des nombres duaux, \textit{C. R. Acad. Sci.} Paris 273A(1971), 1204--1207.

\bibitem[Levine(1985)]{Levinea}
{M. Levine} Bloch's formula for singular surfaces, \textit{Topology},  24(2) (1985) 165--174.

\bibitem[Levine(1985)]{Levineb}
{M. Levine} Torsion Zero cycles on singular
varieties, \textit{Amer. J. Math}., 107(1985), 737--757. 

\bibitem[Levine(1999)]{Levinec}
{M. Levine}\pageoriginale On the $K$-groups of surface singularities, Preprint. 

\bibitem[Milne(1982)]{Milne}
{J. Milne} Zero cycles on algebraic varieties in non-zero characteristic: Rojtman's theorem, \textit{Comp. Math}., 47(1982).

\bibitem[Milnor(1971)]{Milnor}
{J. Milnor} \textit{Introducation to Algebraic K-theory}, Ann. Math. Studies No. 72, Prinecton Univ. Press, Princeton (1971).

\bibitem[Mumford(1968)]{Mumford}
{D. Mumford} Rational equivalence of $0$-cycles on algebraic surfaces, \textit{J.Math. Kyota Univ}., 9(1968) 195--240.

\bibitem[Murthy(1976)]{Murthy}
{M. P. Murthy and R. G. Swan} Vector bundles on affine surfaces, \textit{Invert. Math}., 36(1976) 125--165.

\bibitem[Perdrini(1983)]{Pedrini}
{C. Pedrini and C. Weibel} K-theory and Chow groups of singular varieties, to appear in proceedings of the AMS $K$-theory Conference, Boulder (1983). 

\bibitem[Quillen(1973)]{Quillen}
{D. Quillen} Higher Algebraic $K$-theory, \textit{Lecture Notes in Math}. No. 341, Springer-Verlag, New York (1973). 

\bibitem[Roitman(1972)]{Roitmana}
{A. A. Roitman} Rational equivalence of $0$-cycles, \textit{Math USSR Sbornik}, 18 (1972) 571--588. 

\bibitem[Roitman(1980)]{Roitmanb}
{A. A. Roitman} The torsion of the group of $0$-cycles modulo rational equivalence, \textit{Ann. Math}., 111(1980) 553--569.

\bibitem[Srinivas(1982)]{Srinivasa}
{V. Srinivas}\pageoriginale Vector bundels on the cone over a curve, \textit{Compos. Math}., 47(1982) 249--269.

\bibitem[Srinivas(1985)]{Srinivasb}
{V. Srinivas} Zero cycles on a singular surface, I, II, \textit{J. Reine Ang. Math}., 359(1985) 90--105 and 362 (1985) 4--27.

\bibitem[Srinivas(1999)]{Srinivasc}
{V. Srinivas} Modules of finite length and Chow groups of surfaces with rational double points, to appear in \textit{Ill. J. Math}. 

\bibitem[Weibel(1981)]{Weibel}
{C. Weibel} $K$-theory and analytic isomorphisms, \textit{Invent Math}., 61(1981) 177.197.

\bibitem[Srinivas(1999)]{Srinivasd}
{V. Srinivas} Grothendieck groups of polynomial and Laurent polynomial rings, to appear in \textit{Duke Math. J. }

\bibitem[Srinivas(1999)]{Srinivase}
{V. Srinivas} Indecomposable projective modules on affine domains, to appear in \textit{Compos. Math.}
\end{thebibliography}

