\thispagestyle{empty}

\begin{center}
{\Large\bf Advanced}\\[5pt]
{\Large\bf Analytic Number Theory}
\vskip 1cm

{\bf By}
\medskip

{\large\bf Carl Ludwig Siegel}
\vfill

{\bf Tata Institute of Fundamental Research}

{\bf Bombay}

{\bf 1980}

\end{center}
\eject

\thispagestyle{empty}
\vfill

\begin{center}
\copyright \quad {\bf Tata Institute of Fundamental Research,} 1980


\vfill

\parbox{0.7\textwidth}{No part of this book may be reproduced
in any form by print, microfilm or any
other means without written permission
from the Tata Institute of Fundamental
Research, Colaba, Bombay 400 005.}
\vfill

Printed by M.N. Palwankar at the Press Limited, 414,\\ Veer Savarkar
Marg,

Bombay 400 025, and Published by K. G. Ramanathan for Tata Institute
of Fundamental Research, Bombay 400 005.
\vfill 

Printed In India
\end{center}

\eject

\chapter{Foreword}


``{\em Advanced Analytic Number Theory}'' was first published by the
Tata Institute of Fundamental Research in their Lecture Notes series
in 1961. It is now being made available in book form with an
appendix--an English translation of Siegel's paper ``Berechnung von
Zetafunktionen an ganzzahligen Stellen'' which appeared in the {\em
  Nachrichten der Akademie der Wissenschaften in G\"ottingen,
  Math-Phy. Klasse.} (1969), pp.\@ 87-102.  

\medskip


We are thankful to Professor Siegel and to the G\"ottingen Academy for
according us permission to translate and publish this important
paper. We also thank Professor S.\@ Raghavan, who originally wrote the
notes of Professor Siegel's lectures, for making available a
translation of Siegel's paper.
\vskip 1cm

\hfill {\large\bf K.\@ G.\@ Ramanathan}
\vfill
\eject



\chapter{Preface}


During the winter semester 1959/60, I delivered at the Tata Institute
of Fundamental Research a series of lectures on Analytic Number
Theory. It was may aim to introduce my hearers to some of the
important and beautiful ideas which were developed by L.\@ Kronecker
and E.\@ Hecke.

Mr.\@ S.\@ Raghavan was very careful in taking the notes of these
lectures and in preparing the manuscript. I thank him for his help.
\vskip 1cm

\hfill {\large\bfseries Carl Ludwig Siegel}
