\chapter{Integral Equations}\label{chap21}

\begin{defi*}
A\pageoriginale function $b:R^{d}\to R^{d}$ is said to be locally
Lipschitz if given any $x_{0}\in R^{d}$ there exists an open set
$U_{0}$ containing $x_{0}$ such that $b|_{U_{0}}$ is Lipschitz.
\end{defi*}

\setcounter{exercise}{0}
\begin{exercise}\label{chap21-exer1}
$b$ is locally Lipschitz iff $b|_{K}$ is Lipschitz for every compact
  set $K$ i.e. iff $b|_{K}$ is Lipschitz for every closed sphere $K$.
\end{exercise}

\begin{exercise}\label{chap21-exer2}
Every locally Lipschitz function is continuous.
\end{exercise}

\begin{theorem*}
Let $b:\mathbb{R}^{d}\to \mathbb{R}^{d}$ be locally Lipschitz and
$X:[0,\infty)\to   \mathbb{R}^{d}$ continuous. Then
\begin{enumerate}
\renewcommand{\theenumi}{\roman{enumi}}
\renewcommand{\labelenumi}{\rm(\theenumi)}
\item the equation
$$
Y(t)=X(t)+\int\limits^{t}_{0}b(Y(s))ds\q (*)
$$
has a continuous solution near $0$, i.e. there exists an $\epsilon>0$
and $a$ continuous function $Y:[0,\epsilon]\to R^{d}$ such that the
above equation is satisfied for all $t$ in $[0,\epsilon]$.

\item (Uniqueness) If $Y_{1}$, $Y_{2}$ are continuous solutions of the
  above equation in $[0,T]$, then
$$
Y_{1}=Y_{2}\q\text{on}\q [0,T].
$$ 
\end{enumerate}
\end{theorem*}

\begin{proof}
(ii) (Uniqueness) Let $f(t)=|Y_{1}(t)-Y_{2}(t)|$. As $Y_{1}$, $Y_{2}$
  are continuous, there exists a $k>0$ such that $|Y_{1}(t)|$,
  $|Y_{2}(t)|\leq k$ for all $t$ in $[0,T]$. Choose $C$ such that
  $|b(x)-b(y)|\leq C|x-y|$ for $|x|$, $|y|\leq k$ and
  $C\sup\limits_{0\leq t\leq T}f(t)$. Then $f(t)\leq C$ and $f(t)\leq
  C\int\limits^{t}_{0}f(s)ds$\pageoriginale so that $f(t)\leq
  \frac{(ct)^{n}}{n!}$ for all $n=1,2,3,\ldots$. Thus
  $Y_{1}(t)=Y_{2}(t)$, proving uniqueness.

(i) (Existence) We can very well assume that $X(0)=0$. Let
  $a=\inf\{t:|X(t)|\geq 1\}$,
$$
M>\sup \{|b(x)|:|x|\leq 2\},\q \alpha=\inf\{a,\frac{1}{M}\},
$$
$C\neq 0$, a Lipschitz constant, so that $|b(x)-b(y)|\leq C|x-y|$ for
all $|x|$, $|y|\leq 2$. Define the iterations $Y_{0},Y_{1},\ldots$ by
$$
Y_{0}(t)=X(t),\q Y_{n+1}(t)=X(t)+\int\limits^{t}_{0}b(Y_{n}(s))ds
$$
for all $t\geq 0$. By induction, each $Y_{n}$ is continuous. By
induction again, $|Y_{n}(t)-X(t)|\leq Mt$ for all $n$, $0\leq t\leq
\alpha$. Again, by induction $|Y_{n+1}(t)-Y_{n}(t)|\leq
\frac{M}{C}\frac{(Ct)^{n+1}}{(n+1)!}$ for $0\leq t\leq \alpha$. Again,
by induciton $|Y_{n+1}(t)-Y_{n}(t)|\leq
\frac{M}{C}\frac{(Ct)^{n+1}}{(n+1)!}$ for $0\leq t\leq \alpha$. Thus
$Y_{n}(t)$ converges uniformly on $[0,\alpha]$ to a continuous
function $Y(t)$ which is seen to satisfy the integral equation.
\end{proof}

\begin{remark*}
Let $X:[-\delta,\infty)\to \mathbb{R}^{d}$ be continuous where $\delta>0$. Then
  a similar proof guarantees that the equation (*) has a solution in
  $[-\epsilon,\epsilon]$ for some $\epsilon>0$.

Define $B(X)=\sup \{t:(*)$ has a solution in $[0,t]\}$. The theorem
above implies that $0<B(X)\leq \infty$. $B(X)$ is called the {\em
  exploding time}.
\end{remark*}

\begin{remark*}
If $b$ is, in addition, either bounded or globally Lipschitz,\break
$B(X)=\infty$ for every continuous $X:[0,\infty)\to \mathbb{R}^{d}$.
\end{remark*}

\begin{example*}
Let\pageoriginale $b(y)=y^{2}$, $X(t)=0$. The equation
$$
Y(t)=x_{0}+\int\limits^{t}_{0}b(y(s))ds
$$
with $x_{0}>0$ has a solution
$$
Y(t)=\frac{1}{\frac{1}{x_{0}}-t},\ \forall t<\frac{1}{x_{0}};
$$
the solution explodes at $t=x^{-1}_{0}$.
\end{example*}

\begin{prop*}
If
$$
B(w)<\infty,\q \text{then}\q \Lt\limits_{t\uparrow
  B(w)}|y(t)|=+\infty.
$$
\end{prop*}

\begin{proof}
Suppose that $\varliminf\limits_{t\to B(w)}|y|=R<\infty$. Let
$(t_{n})$ be a sequence increasing to $B(w)$ such that $|y(t_{n})|\leq
R+1$, $\forall n$. Let
$$
\tau_{n}=\inf\{t\geq t_{n}:|y(t)-y(-_{n})|\geq 1\}.
$$

Then
\begin{align*}
1 &= |y(\tau_{n})-y(t_{n})|\\
&\leq w(\tau_{n})-w(t_{n})|+(\tau_{n}-t_{n})\sup
|b(\lambda)|\ldots,\ (1)\\
&\qq \lambda\in S(y(t_{n}),1).
\end{align*}

Since $(t_{n})$ is bounded, we can choose a constant $M$ such that
$$
|w(t_{n})-w(t)|<\frac{1}{2}\q\text{if}\q|t-t_{n}|\leq M.
$$

Then using (1),
$$
\tau_{n}-t_{n}\geq \inf\{M,(2\sup|b(\lambda)|)^{-1}\q\text{where}\q
\lambda\in S(Y(t_{n});1)
$$

Therefore
$$
\tau_{n}-t_{n}\geq \inf (M,(2\sup |b(\lambda)|)^{-1},\lambda\in
S(0;R+2))=\alpha(\text{say})\forall\ n.
$$\pageoriginale

Chose $n$ such that $\tau_{n}>B(w)>t_{n}$. Then $y$ is bounded in
$[t_{n},B(w)]$ and hence it is bounded in $[0,B(w))$. From the
  equation
$$
y(t)=X(t)+\int\limits^{t}_{0}b(y(s))ds
$$
one then gets that $\Lt\limits_{t\to B(w)}y(t)$ exists. But this is
clearly a contradiction since in such a case the solution exists in
$[0,B(w)+\epsilon)$ for suitable $\epsilon$, contradicting the
  definition of $B(w)$. Thus
$$
\varliminf\limits_{t\to B(w)}|y(t)|=+\infty
$$
and hence
$$
\lim\limits_{t\to B(w)}|y(t)|=+\infty.
$$
\end{proof}

\begin{coro*}
If $b$ is locally Lipschitz and bounded, then $B(X)=\infty$ for all
$X$ in $C([0,\infty),\mathbb{R}^{d})$.
\end{coro*}

\begin{proof}
Left as an exercise.
\end{proof}

\begin{prop*}
Let $b:\mathbb{R}^{d}\to \mathbb{R}^{d}$ be locally Lipschitz and
bounded. Define 
$T:C([0,\infty),\mathbb{R}^{d})\to C([0,\infty),\mathbb{R}^{d})$ by $TX=Y$ where
$$
Y(t)=X(t)+\int\limits^{t}_{0}b(Y(s))ds.
$$

Then $T$ is continuous.
\end{prop*}

\begin{proof}
Let $X$, $X^{*}:[0,\infty)\to \mathbb{R}^{d}$ be continuous, $K>0$ be
  given. Let $Y_{0},Y_{1},\ldots,Y_{0}^{*},Y^{*}_{1},\ldots$ be the
  iterations for $X$, $X^{*}$ respectively. Then $|Y_{n}(t)-X(t)|\leq
  K||b||_{\infty}$ for $0\leq t\leq K$, $n=0,1,2,3,\ldots$, so that we
  can find $R$ such that $|Y_{n}(t)|$, $Y^{*}_{n}(t)|\leq R$ for
  $0\leq t\leq k$, $n=0,1,2,\ldots$,\pageoriginale Let $C\geq 1$ be
  any Lipschitz constant for the function $b$ on $|x|\leq R$. Then
\begin{align*}
& |Y_{n}(t)-Y^{*}_{n}(t)|\leq \sup\limits_{0\leq t\leq
    K}|X(t)-X^{*}(t)|\cdot (1+Ct+\frac{(Ct)^{2}}{2!}+\\
& +\cdots +\frac{(Ct)^{n}}{n!})\quad\text{for}\quad 0\leq t\leq K,\q
  n=0,1,2,3,\ldots .
\end{align*}

A $b$ is bounded, $Y_{n}$ converges uniformly to $Y$ on
$[0,K]$. Letting $n\to \infty$, we get
$$
\sup\limits_{0\leq t\leq K}|(TX)t-TX^{*})t|\leq
e^{ck}\sup\limits_{0\leq t\leq K}|X(t)-X^{*}(t)|,\ldots(2)
$$
where $c$ depends on $\sup\limits_{0\leq t\leq K}|X(t)|$,
$\sup\limits_{0\leq t\leq K}|X^{*}(t)|$. The proof follows by (2).
\end{proof}
